\section*{Journal Stream Started 2015.08.21}

\subsection*{\#loveLife}
This is some stuff. The stuff is words, really. The amazing thing is I get to string them together however I please.

I am so in love because of who Amanda Chadderdon is and how lovingly Amanda has behaved toward me. I am scared to tell her this because I think it may scare her off. I don't know what to do.

I say "I'm not sure what to do" as though, and I want to joke that "I \textbf{AM} sure I'll be happy however my life pans out." but I say "I'm not sure" as though...I LOST THE THOUGHT OVER THE COURSE OF HOURS...

\subsection*{\#lifePlan}
I wanna journal about what I'll do with my life. I have come to the conclusion that...CONTINUED ON NEXT

\section*{2015.08.21at06:57}
\subsection*{\#lifePlan} CONTINUED FROM YESTERDAY'S THOUGHT:
"I have come to the conclusion that..." I should create a vegan cheese while I'm looking for work and working off student loans as a cab-driver. In order to plan and verify feasability, I calculate some basic time requirements imposed by all the things I want to do(after this table, a current plan is to be kept in tabulated form in weeklyTimeTable.tex):

\begin{table}
\caption{\label{tab:originalWeeklyAndDailyTimeTable}Weekly and Daily Time-Table}
\begin{tabular}{|r|r|l|}
\hline
Hours/Week&Hours/Day&Activity\\
\hline
7&1&hygiene\\
7&1&workout\\
49&12$\times$4+1&drive a cab\\
14&2&social and play time\\
42&6&sleep\\
21&3&study graduate physics courses\\
28&4&journal and invent\\
\hline
\end{tabular}\end{table}

This gives $7 \text{days} \times 24 \text{hours} = 168$ hours per week, accounting for the all hours in a week. I intend to investigate using food, sleep, and drugs to augment my productivity in learning and inventing. Here, inventing can be broadly interpretted.

\subsection*{\#invention}
Invention could mean creating a vegan cheese by chemical synthesizing a substrate with the desired percentages and types of fat, protein, and carbohydrate. Invention could mean designing a belt for runners to store an empty or full water bladder in, as well as shopping bags, a phone, pens, keys, clean and dry clothes, and other items. Invention could mean designing a pair of gloves with all the things listed for the belt attached as well as carrying pouches to provide runners with an ergonomic upper-body workout while running.

\section*{2015.08.26at15:18}
\subsection*{\#invention, \#softwareInScience, \#hackingForScience}
Make idealab: a database of possibly networked ideas, unsolved problems, and solutions which are easily searched by users. An idea of a use-case: lab A at some institution has a problem which impedes its progress and so it checks with idealab for a solution. Because the solution to this probelem hasn't been catalogued in an appropriately findable manner, lab A submits this problem to idealab.

Lab B has problem P. Lab B searches for a solution using standard methods. lab B finds lab A's record of problem P on ideaLab. Lab B registers another incidence of problem P.

IdeaLab has a system...

\section*{2015.08.27at22:53}
\subsection*{\#invention, \#softwareInScience, \#hackingForScience, \#ideaLab}
{\bf Continued from 2015.08.26at15:18}
IdeaLab has a system to rank ideas relative to one another. An idea's rank is a function that increases with the number of users who had this idea. Rank increases with the number of viewers it has.

Think of additional variables that rank varies with. The single most important task in creating ideaLab is to make idea browsing and discovery of ideas work well. IdeaLab is a great way to bring ideas of how to help the human endeavor to the layperson.

Suppose Bob the bricklayer has an idea which helps Portland Cement make a better cement. If only there was a framework for the sharing of ideas to be witnessed and paid for as a percentage of calculated increased profit. Players are motivated to pay handsomely for ideas to encourage new ideas. This an alternative to a conventional research and development department,

IdeaLab's job in this is:  provide the easy access to the hosted ideas, problems, and solutions.[I wanted to add more here about idealab and I wanna work on the idealab site as a web-app. Make this as a ruby, php, or python site.]

\section*{2015.08.31at14:35}
\subsection*{\#journal, \#DIY-ence, \#ideaLab}
People can run independent studies and experiments by throwing food to a group of ducks and recording the responses of the groups. When observing a small group, it seems to observe whether there is altruism displayed. For example, when a large clump of bread is thrown to the group, does the group let all members get some part of the clump or do the dominant ducks hoard the resource?

I want to read "open access" journals. This will keep me up on subject matters' current evolution.

\section*{2015.09.15at20:15}
\subsection*{\#journal}
I find myself wondering why are kthese prople the way they are. This is about the most ridiculous thing Ive seen. I have finally made myself come out and write and I actually am thinking "this is all I can come up with."

Language is a beautiful "arbitrary," as in "it was decided," and "mysterious," as in "what things can a study of this thing[, language,] tell us about nature. It beautiful that a finite set of symbols and rules can describe such a seemingly infinite set of things. This is a beauty worth exploring.

\subsection*{lyrics}
She's so sweet but I'm just me.
She never told me what to be.
If I am wrong then that's me and that's all that we'll be, but I love her.
Then I'm gone and that's all that I'll see of her.

What's there to love when she's gone?
I can't say what's not there.
I'm here.
I'll love me.
I love me.
I love to be
everything
never mean
know what I mean?

\section*{2015.10.09at10:15}
\subsection*{ \#schedule \#ideaConsulting }
I have decided to fulfill my dreams with the time scheduled for sleeping. This means I will read interesting and promising books with this time. I will write my thoughts and video record journals when necessary because typing can't keep up with the rate of my thoughts.

On that note, I should start playing with a typing tutor. I want to find a good one. Back to a thought from the previous paragraph, Google could make software for video journaling.

When thinking about the idea of an unaffiliated, freelancing individual having ideas that benefit a company, I think I should pioneer an industry I dub idea consulting.

\section*{ 2016.01.05at14:28 }
\subsection*{ \#inDefenseOfPeace }

I have not seen a disagreement that I thought was worth lives. Does fighting make a person tough? Forfeiting thinking for fighting appears to turn righteousness into wrongfulness. Can we think of a better way?

What if we use the money, energy, and passion currently dedicated to an ironically named Department of Defense to find appropriate resolutions to problems? What are you willing to spend to find resolutions which don't cost lives to raise hate?

Peaceful resolutions may be hard to find. People commend soldiers for participating in fights we all fund. What if people spent the same money and lives on clever diplomacy that avoids wars? What if we use love to spread love?

One idea is to reward diplomacy. What if there was a system to which any person can contribute diplomatic ideas and be rewarded for bringing a good idea? What if people could work together to find an elusive peaceful resolution?

Wikipedia's Software Industry article reads "according to industry analyst Gartner, the size of the worldwide software industry in 2013 was US\$407.3 billion." Even in this well funded industry, many of the most effective tools are created and actively maintained by thousands of volunteers. I am talking about open-sourced software.

The term opensource refers to software whose source-code is freely editable. This allows any person to contribute a resolution to any issue. In this way, the opensource community offers competitive solutions which are licensed to remain freely editable by posterity.

Can opensource show us how to collaborate on ideas for peaceful resolutions? Opensource provides solutions which competed with with the leading products of a US\$400 billion industry with notable successes. Opensource software dominates the market for web servers and secure cheap personal computing playgrounds.

\section*{ 2016.02.02at22:13 }
\subsection*{ \#mathematicalBreadcrumbs }
I hope that each who is in wonder at the majesties of either math or science one day realizes the beauty that complex exponentials store the arbitrary but beatifully succinct connection between algebra and rotations.

\section*{ 2016.02.06at18:34 }
\subsection*{ financialPlannery investmentStrategy }
Plan to save money at the rate $R$ dollars per time period(e.g. year, month, week, day,..). Put money away in savings in quantity $S$. Purchase in quantity $P$ for repairing the house with top quality fixes that increase equity or other acts which increase assets.

The killer idea here is to count asset-increasing-work as money saved in case saving everything over a reasonable spending limit doesn't work. This is, however, the preferred saving plan: 
\begin{itemize}
\item spend within spending limit $L$;
\item let $E$ be the amount earned during the period;
\item let $J$ be the current project, E.G. 
\item $E = $
\end{itemize}

With these definitions let $R=S+P$. 

\section*{ 2016.02.14at23:38 }
\subsection*{ addictedToLearning }
I want to be someone who is addicted to learning. I want to meet someone who is addicted to learning. I specifically want to meet someone who is on trajectory to know physics and computer science.

\section*{  2016.02.27at16:47 }
\subsection*{  \#stolenJournalingTime }
It strikes me while trying to journal right now that I need to script the journaling process better. I need to make kydate return a string with no newlines in it. I think echo wraps a cstring in newlines.


\section*{ 2016.03.19at03:14 }
\subsection*{ testJournal.txt fascinatingTopic alsoFascinating }
This is truly some kind of shit. I cant type on my chromebook becasue there was this really cool idea somebody had to be clever by making the trackpad's scrollwheel (the... I had just forgotten to run my trackpad configuration tool after restarting the chromebook.

\#iRemember

\section*{ 2016.03.19at12:19 }
\subsection*{ \#hashtags \#reviewingLastEntry }
hahah, looking at the above, I forgot what I had remembered momentarily. At least I see it as funny, bordering on hilarious. I think this is a great way to handle something that might be heartbreaking if handled differently. This is a good example of how to emotionally handle lost wonderful ideas. 

\section*{ 2016.03.27at22:36 }
\subsection*{ millionDollarIdea }
I want to start a music hosting company with a stated mission to "make money in a way that doesn't hurd the freedom of the music."

Business plan:
Host a library of music, books, guides, tutorials, and other works that people want to self-publish. Hosted parties may choose a license for their works. Perhaps model monetization openly after github: users must pay for storage of their work to license the work as closed-to-derivative-works. 

\section*{ 2016.03.27at23:21 }
\subsection*{ whatDidILearnFromPhysics aLetterToThoseComingAfter }
I learned that approximations which describe a phenomenon to first order are a fine starting place to build an understaning of the phenomenon. I found from this that observations of first oder behavior are a fine place to begin observation. The lesson of the power of the first orders I've learned through many related lessons.

I learned that "limiting cases are a physicist's bread and butter," said some physics professor at OSU. I have found several situations where this statement resounds in my memory. One application I have developed great affection for is in deciding how to make a first guess at a model for observed phenomena.

Using these two teachings together, one can make useful guesses at the behavior of phenomena. From a first order observation, one knows the limiting behavior of $f(x)$ for both decreasing and increasing $x$. This is considered an observation of the behavior of $f(x)$ to first order in $x$.

Notice I said a lot of words to describe what has been observed. All these words have meaning. It is enlightening to know the significance of every single word when a person speaks purposefully.

There are a calculated number of degrees of freedom removed from a general function one may observe to first order in one of its independent variables. Some examples of the behavior of $f(x)$ to first order in $x$ follow.

\begin{itemize}
\item The value of $f$ may increase as the variable $x$ increases:$$f(x_2) > f(x_1) \Leftrightarrow x_2 > x_1.$$ This is said "$f$ varies directly with $x$."
\item The value of $f$ may decrease as the variable $x$ decreases:$$f(x_2) < f(x_1) \Leftrightarrow x_2 < x_1.$$ This is said "f varies inversely with $x$."
\item The value may behave stochastically, chaotically, but always functional. Functional because $f(x)$ always has the same value. Every day of the week.

One way to say this logically and in a way which requires and might teach some, mathematical vocabulary:
"The function $f()$ is a bijective function. $f(x_0)$ is a single value for a single value of $x_0$."(I didn't remember what I started writing...I just came back and it's now time for another quick \\openinglst\$journal\\closedalsting-ing.
\end{itemize}

\section*{ 2016.03.31at00:21 }
\subsection*{\#{million dollar idea}}
Talk to Ryan [Parmeter, 2016.03.31at06:14]about google getting behind the command line for usability. People who use the command line fall in love with computers. A couple different ways of going about this are to deliver hardware along with drivers.

This could be called a platform(here's a golden idea for a product name: a springboard).

\section*{ 2016.03.31at23:00 }
\subsection*{\#{stream of consciousness} \#anneFilson } 
Write to Anne Filson to schedule some coffee at lunch-time. I want to write a note asking for a coffee and a conversation. Some things I want to discuss are listed here.

I want to mention gut flora possibly needing the bacterial byproducts of fermentation. I want Anne's input about the data pertaining to the hominin diet. What do we know about homini and human diet throughout the evolution of our species.

This could be a beneficial topic for someone trying to get his message of veganism out to a large audience. This could also be a publishable work: people possibly used to fill their bellies beyond full to both get bacterial growth in the intestines. This thought occurred to me when I noticed after a day of overeating that my belch tasted like alcohol(This was within a month of falling off my bicycle and breaking out my front teeth following a night of drinking and swearing off drinking (except for Rich Tehan's birthday in 2016)).

\section*{ 2016.04.01at11:58 }
\subsection*{\#\{million dollar idea\}}
Discuss the following ideas I've had with Ryan Parmeter, who is a friend from the hesper.net building that Ryan Schrink ran and drained the rainwater out of the ceiling's insulation by pushing a broom up into the plastic layer covering the bottom of the insulation-packs(it was packs similar to, if not exactly, interstud insulation from exterior wall insulation).

Collaborate with Google in a way that gives me more power as an "inventor" to get my ideas out so the ideas may better benefit humanity. I have four ideas now that I want to write here before I forget them for Google, including the corporation-and-inventor-collaboration mentioned above.  

\section*{ 2016.04.02at15:14 }
\subsection*{\#millionDollarIdea}
The items I wanted to address with Ryan Parmeter to present to Google with a witness are those following. I want to have a witnessed meeting with executives from Google to present ideas for Google to use, cutting me some originator's percentage of the profits for the first few years. Ryan could serve as my witness.

Google could make a device and the software to provide functioality like the nest home-control device. This device would serve as an upgrade to older vehicles to provide the features of newer cars as well as any feature that people dream up. Example features are navigation systems, phone interface systems, backup cameras, and antitheft features. This serves as something the EPA might be interested in endorsing because upgrading cars' features would presumably reduce waste by slowing the rate at which cars are disposed of.

Google could offer a feature I call a "sensible text-size" in chrome to detect a main text-display-elements of webpages. Sensible text-size uses the number of characters per line known to be optimal from typesetting. I think this value is 55 to 65 characters per line.

Once this happens, I guess that others would make their implementation of this feature. I imagine that consequent to browsers and power users implementing this feature web design best practices would evolve to evolve to cater to this feature. This feature would allow for command-line-browsing, which propogates the UNIX paradigm of embracing a text-stream as the perfect data-structure.

The efficiency gains in computer-use from implementing the UNIX philosophy segues nicely into the final idea which I am most excited about: Google supplies a chromebook that is made to host crouton. Preferably, Google supplies the drivers for use in a standalone linux installation, so that users don't have to use up resources keeping ChromeOS loaded. Google could mandate that hardware manufacturers supply drivers for their devices to the open-source-community. 

\section*{ 2016.04.11at07:45 }
\subsection*{millionDollarIdea}
Google could lead the way in voice recognition technologies by using veiwers' corrections to Youtube's auto-generated captions. This would also be a wonderful benefit to those suffering from a disability which puts them in need of the captions or even transcripts from a video. It is not terrible wild to imagine a system which could give captions in realtime.

\section*{ 2016.04.19at23:45 }
\subsection*{streamOfConsciousness}
I finally made myselfsit down and write. thoughts are thinking much faster than the words get set in type. I need to do typing eercises to rectify this. Now I've had the idea that I've had before: I can journal when I have a decent thought during the time I am 

\section*{ 2016.04.22at13:26 }
\subsection*{restaurantBestPractices}
Restaurants that offer outdoor seating that might get rained on could let customers dry off their chosen seats with a pile of laundry set out at a self-service station which also offers flavoring mixes, self-busing bins, utensils, and garbage.

\section*{ 2016.04.22at13:32 }
\subsection*{amusumentParkBusinessPlan}
I want to create a restaurant attached dog park attached to human-powered amusement rides attached to a large host of other attractions. The place should have a part of the restaurant where the people can watch their children and dogs playing in their respective playgrounds and in each others' playground. 

\section*{ 2016.04.20at22:16 }
\subsection*{journalingWhileHigh}
I propose the following activity to myself. My proposal will will start to sound something like the beginning of a book. That last sentence just seems like a hint and so I wonder if I'll wonder at some point in my life when I first realized writing will be the point of my life's work.

I shall start walking every day; getting envigorating exercise multiple times a week. I don't need hobbies to fill up my time because I have the obligation to myself of having thought of living an experiment in health as an example to my fellow people.

People are not humans. I mean this as people are not the blood, flesh, and bone that comprises the physical body of a person. Here I think person as the singular form of people. People are the tiny, apparently singular spark in the brain that is, nevertheless the product of a concerted effort on a statistical number of cells. I make the following broadly generalized statement as a guess at something possibly worth investigating at a later time: the mystery of life can, following from the last sentence be said to be shadowed from our understanding by statistics.

I am in the middle of writing a letter, of course on Facebook, to the physics girl proposing we make educational videos on a host of topics for free to help all people's existence. I am arguing that this will benefit in...I want to revisit several issues in this entry. 

\section*{ 2016.05.02at00:47 }
\subsection*{ lifePlan research academicPlan }
I want to do a project which revolutionizes education in physics and other subjects. It is a jupyter notebook with embedded video built right in. Mining the data from this to further physics education research is a promising motivation of this research. This environment can clearly be used for any other subject.

The multimedia learning resource can be any medium, whether slides with audio, only audio, or video. I can take this idea to professors Roundy, Manogue, Qiu, 

\section*{2016.05.03at21:13}
\subsection*{iWantToWritebABook}

\section*{ 2016.05.13at23:05 }
\subsection*{ gottaTakeThisStreamDown }
[2016.01.15@21:39 oops, I guess I missed that one...bummer, dude:-[]


\section*{ 2016.06.15at21:41 }
\subsection*{ artificialScience thatLastOneIsFunnyBut getKyleInScience then getKyleNScience }
I have an idea I want to pursue.
I suspect Roundy could be helpful in this.
I want to develop a way for humans to get more intimate with the beauty that computers can provide through:
\begin{enumerate}
\item interacting with a beautiful operation system;
\item creating a logical entity as a pet with that operating system that is everywhere and can do anything between, alongside and through its host(computer)'s inputs and outputs;

\section*{ 2016.06.15at21:54 }
\subsection*{ ideasForScientificInvestigation }
I want to investigate something I will describe starting with the particular example whose consideration led me to think of the object of the investigation I hope to pursue.
Let a hollow glass cylinder be filled with a given liquid.
Orient the cylinder so its axis is vertical and close the top of its hole.

This liquid has an interesting property that appears on consideration to be characteristic of the liquid's mass density per unit of force of interparticle attraction.

That property is the distance which a unit mass will fall under its own weight.

\section*{ 2016.05.18at23:30 }
\subsection*{iNight(lyRoutine)}

\section*{ 2016.05.19at08:55 }
\subsection*{coffeeCommuteAllenBrosOnMonroe}
I would like to take the idea of putting linux on a chromebook to Google. The hardware supports me sitting in the sun and type 16 hours on a single charge. With a linux backend, this blows away anything currently sold as a laptop.

\section*{ 2016.05.19at18:41 }
\subsection*{streetWisdom}
A friendly street-musician named Daniel Faulk remarked a very true statement: "[it is easier to be creative when in that place where trying to simultaneously perform two tasks which are each difficult on its own.]" What he said was actually literally closer to "[Soloing is hard. Playing rhythm is hard. When you're in the place between the two you're more creative.]" He said this while telling me he can't do both at the same at the same time.

This leads me to the thought: what if people's burst of creativity when first learning to sing and play or do any two mentally engaging activitiies at the same time.

\section*{ 2016.05.20at11:58 }
\subsection*{physicsIsFun mathematicalFoundationOfExponentialsInStatMech}
Professor Matt Graham at OSU told me something that I want to take down. He said this while teaching ph641:statistical thermophysics that I attended the year after graduating OSU while I was working a coding contract for the EPA. He said that the ubiquitous exponential in statistical thermophyics arises from an ansatz: Stirling's Approximation.

\section*{ 2016.05.20at12:05 }
\subsection*{statMech}
It seems to me at first consideration that it may be the uncoupling of dependence of the quantum states of neighboring water molecules which produces the greater opacity of water in the state of steam than in the state of liquid.

\section*{ 2016.05.25at11:26 }
\subsection*{lateWorkdayMorningRoutine}
I could do wonderful things with a position at Google. I have this idea that they could partner with the opensourced community. As developers in this community form startup interests, Google could selectively partner with them.

This model doesn't have to dominate Google's monetization efforts. This Opensourced-Partnership-Program(OPP?) could nicely complement Google's current marketing technique. Further, OPP provides dan example of Google's old mantra: "don't be evil."

\section*{ 2016.05.26at07:34 }
\subsection*{thursdayMorningCoffee}


\section*{ 2016.05.26at07:51 }
\subsection*{currentLifePlan lifeOneDayPerTime oneDay@aTime oneDayAtATime}
I made a schedule for my work weeks: wake at 5am to beat the sun to hitting the ground; get to work by 6am Monday through Thursday and every other Friday; work until 10:30am Monday through Thursday and every other Friday; take a lunch break, run errands, and journal with remaining time from 10:30am to 1pm; work from 1pm to 5:30pm Monday through Thursday; work from 1pm to 4:30pm on every other Friday.

This schedule works me 40hours every week when weeks are split at noon on Friday. I work 9 hours Monday through Thursday. I work eight hours one Friday. I don't work the next friday.

The plan is to do my nightly routine by 9pm. Nightly routine is meant to include a final smoke-session. I plan to have another smoke-session if aid is needed for sleep. Either way, the plan holds to be in bed with lights out and teeth brushed since my last smoke by 11pm.

\section*{ 2016.05.29at19:32 }
\subsection*{dinnerAtSterlings}
I was remembering that Portugal has "decriminalized" all drugs [Todd asked me to put electronics away. 2016.05.31@11:00:00]

\section*{ 2016.05.31at11:07 }
\subsection*{personalJournal}
I have stopped into Allen Bros on 26th and Arnold before going to work. I just got done with a partial root canal with the dentist at the Corvalis Gentle Dental. He stopped part of the way through the root canal because he wasn't confident proceeding. His office referred me back to the Gentle Dental in Salem called Gentle Dental at Idlewood.

Idlewood is the office of Wayne Van de Graaf, the oral surgeon who reimplanted my front teeth. This was the morning that I had crashed at around 1am. Dr. Treloar at Corvallis's Good Samaritan ER had originally placed my teeth back in their sockets quickly in hopes of the teeth surviving.

It turned out that Dr. Treloar had replaced the teeth in the incorrect positions and directions. I feel grateful that Treloar had done such a caring and careful job as he did in helping me deal with the consequences of my morning's drunken bike ride from the bar. In order to do my part, I resolved to stop drinking and have been successful other than a shot at Richard Tehan's birthday and a sip of beer at Amanda Tyree's bidding while sitting on Bastendorf Beach watching unrideably small surf with her and Sterling.

I believe I have journaled this before, but I want to say this again: I don't want to drink. Abstinence from alcohol is motivated by a desire to maintain and imrove my health, a desire to be more productive than I am when I drink, and for safety. Falling off my bike and knocking my teeth out was not my first lesson about safety and drinking. I plan to make this incident my last.

\section*{ 2016.06.01at08:11 }
\subsection*{portlandForTheEndodontist}

Below is a table that revisits the weekly plan that was made in a previous post.

\begin{table}
\caption{\label{tab:2016.06.01WeeklyAndDailyTimeTable}Weekly and Daily Time-Table}
\begin{tabular}{|r|r|l|}
\hline
Hours/Week&Hours/Day&Activity\\
\hline
7&1&hygiene\\
7&1&workout\\
49&12$\times$4+1&work\\
14&2&social and play time\\
42&6&sleep\\
21&3&study\\
28&4&journal and invent\\
\hline
\end{tabular}\end{table}

\begin{table}
\caption{\label{tab:2016.06.01DailySchedule}Daily Schedule}
\begin{tabular}{|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|}
\hline
1&2&3&4&5&6&7&8&9&10&11&12&13&14&15&16&17&18&19&20&21&22&23&24\\
\hline
&&&4:30 wake&5:00 commute\\5:20 workout\\5:40 shower&6 work&&&&10:30 lunch&&&13 work&&&&5:30 leave work&&&&&&&\\
\hline
\end{tabular}\end{table}

\begin{enumerate}
\item 6:00 - wake
\item 6:20 - commute
\item 6:40 - workout
\item 7:20 - shave and shower
\item 7:45 - eat
\item 8:00 - work
\item 11:00 - lunch
\item 11:30 - work
\item 2:30 - walk
\item 3:00 - work
\item 6:00 - get off
\end{enumerate}

\section*{ 2016.06.11at14:11 }
\subsection*{responsiblePackaging suggestionsToIndustry pleaseProduceReusableContainers youAlreadyPackageThings}
What would happen if humans began to create things in a nondisposable fashion? What if we began creating packaging for groceries that could be washed and reused as household Ziploc-bags or for fruit and goods at another market. Potatos could be packaged in bags that could work as sacks to chuck random camping or gardening items into.

If these things are reusable and they are made of high enough quality that people wanted to keep them around and reuse them for stuff then it would be good PR for the company.

\section*{ 2016.06.12at14:55 }
\subsection*{softwareIdea InterfaceIdeaReally}
I want to make a multimedia editing visual interface that displays a waveform for the audiotracks zoomed to any region of interest. Users could pinch to zoom the region of interest, lay layers of effects which are visible in a tagged region specified by a brace. The sound filters should be able to be added, ordered and removed atomically.

Users can play the visible region or a tagged subregion. Tagging of subregions can be similar to tagging regions where effects are applied. Effects that start and end at the same time should be tagged together.

\section*{ 2016.06.17at19:52 }
\subsection*{ideaToEndWoefulStateOfPublicHealthPoliticalCorrectness}
I want to speak with Allan Thornhill, the newly appointed chief of the Western Ecology Division(WED). I could speak with with my immediate supervisor, Allen Brookes. Tertiarily, I could speak with the contractor in charge of the project with the fegs-dashboard, Kirsten Winters. Quaternarily, I could speak with one of my cubicle-mates, either Colleen Barr, Patrick Winger, or Vladimir Pedovic.

Really, I should speak to everyone I can. Being strategic about whom I tell my good ideas is more selfish than I like to perceive myself. It is a dance, as, at this moment, it feels like everything is, a dance. This dance is balancing economy of effort and sharing my ideas as much as possible.

I want to propose the idea to make it politically incorrect to feed people animal-products in the same way it is politically incorrect to exclude people with disabilities. This idea comes to me from being outraged that general employee-funds are being spent to provide animal products for food at an EPA function.

It is my opinion that the WED needs to make a bold move to act outside the connotations of its scope. By this I mean that WED needs to concern itself with human endeavor. People are part of the ecology of their region. People are animals. It is pompous, arrogant, conceited, flawed, and dangerous to not model human animals as part of ecosystems.

We need to address the conflict of interest the USDA has with disseminating health information. 

The study results are in. The evidence is published. Why does public-policy allow people's education in nutrition to be led by agricultural interests.

\section*{ 2016.06.17at20:18 }
\subsection*{emotionalOscillationIsAThingThatDescribesCausalChemicalPathways}

\section*{ 2016.06.17at20:21 }
\subsection*{calculateTheLengthOfAPlaneThatAppearsAsLongAsAQuarterInchArm'sLengthFromMyEye}

\section*{ 2016.06.26at15:22 }
\subsection*{somethingToRemember conversationWithMom}
Oops,i forgot.

\section*{ 2016.07.03at12:08 }
\subsection*{myLifesWork}
Being Nice is my life's work.

\section*{ 2016.07.03at12:12 }
\subsection*{theOnlyCorrectPronunciation}
The only correct pronunciation is the one the speaker judges to be the best.


\section*{ 2016.07.17at22:17 }
\subsection*{ #writtenWithBlahScript }
iHaveSpentMyLifeOnThis inventSomeClassNamedAbstractics abstractricsBecomesAbstractrix

\section*{ 2016.07.17at22:19 }
\subsection*{LaTeX}
Sometimes my journal is written in the mode of me telling myself to do things. The following will be a brain dump of thoughts I've recently entertained. Note to self: get your parser ready.

I want to play with evolution by throwing out every kind of flower- and delicious edible fruit seeds at parks. We put money into homeless shelters when we could just grow edible plants in public spaces. Caring for society's people, stated people in general because rich and poor people alike might forage the local spaces, could become an endeavor that private groups and individuals undertake by leaving community-produce-trees by the side of the road.

\section*{ 2016.07.31at20:03 }
\subsection*{ #writtenWithBlahScript }
deleteme testingBlahScriptAfterLongTimeAwaySoNoKowIfWorks iAm

\section*{ 2016.07.31at20:19 }
\subsection*{ #writtenWithBlahScript }
imReallyGonnaUseMyLaptopToRecordMeInMyLivingRoom
||||||| merged common ancestors
=======
section*{Journal Stream Started 2015.08.21}

\subsection*{\#loveLife}
This is some stuff. The stuff is words, really. The amazing thing is I get to string them together however I please.

I am so in love because of who Amanda Chadderdon is and how lovingly Amanda has behaved toward me. I am scared to tell her this because I think it may scare her off. I don't know what to do.

I say "I'm not sure what to do" as though, and I want to joke that "I \textbf{AM} sure I'll be happy however my life pans out." but I say "I'm not sure" as though...I LOST THE THOUGHT OVER THE COURSE OF HOURS...

\subsection*{\#lifePlan}
I wanna journal about what I'll do with my life. I have come to the conclusion that...CONTINUED ON NEXT

\section*{2015.08.21at06:57}
\subsection*{\#lifePlan} CONTINUED FROM YESTERDAY'S THOUGHT:
"I have come to the conclusion that..." I should create a vegan cheese while I'm looking for work and working off student loans as a cab-driver. In order to plan and verify feasability, I calculate some basic time requirements imposed by all the things I want to do(after this table, a current plan is to be kept in tabulated form in weeklyTimeTable.tex):

\begin{table}
\caption{\label{tab:originalWeeklyAndDailyTimeTable}Weekly and Daily Time-Table}
\begin{tabular}{|r|r|l|}
\hline
Hours/Week&Hours/Day&Activity\\
\hline
7&1&hygiene\\
7&1&workout\\
49&12$\times$4+1&drive a cab\\
14&2&social and play time\\
42&6&sleep\\
21&3&study graduate physics courses\\
28&4&journal and invent\\
\hline
\end{tabular}\end{table}

This gives $7 \text{days} \times 24 \text{hours} = 168$ hours per week, accounting for the all hours in a week. I intend to investigate using food, sleep, and drugs to augment my productivity in learning and inventing. Here, inventing can be broadly interpretted.

\subsection*{\#invention}
Invention could mean creating a vegan cheese by chemical synthesizing a substrate with the desired percentages and types of fat, protein, and carbohydrate. Invention could mean designing a belt for runners to store an empty or full water bladder in, as well as shopping bags, a phone, pens, keys, clean and dry clothes, and other items. Invention could mean designing a pair of gloves with all the things listed for the belt attached as well as carrying pouches to provide runners with an ergonomic upper-body workout while running.

\section*{2015.08.26at15:18}
\subsection*{\#invention, \#softwareInScience, \#hackingForScience}
Make idealab: a database of possibly networked ideas, unsolved problems, and solutions which are easily searched by users. An idea of a use-case: lab A at some institution has a problem which impedes its progress and so it checks with idealab for a solution. Because the solution to this probelem hasn't been catalogued in an appropriately findable manner, lab A submits this problem to idealab.

Lab B has problem P. Lab B searches for a solution using standard methods. lab B finds lab A's record of problem P on ideaLab. Lab B registers another incidence of problem P.

IdeaLab has a system...

\section*{2015.08.27at22:53}
\subsection*{\#invention, \#softwareInScience, \#hackingForScience, \#ideaLab}
{/bf Continued from 2015.08.26at15:18}
IdeaLab has a system to rank ideas relative to one another. An idea's rank is a function that increases with the number of users who had this idea. Rank increases with the number of viewers it has.

Think of additional variables that rank varies with. The single most important task in creating ideaLab is to make idea browsing and discovery of ideas work well. IdeaLab is a great way to bring ideas of how to help the human endeavor to the layperson.

Suppose Bob the bricklayer has an idea which helps Portland Cement make a better cement. If only there was a framework for the sharing of ideas to be witnessed and paid for as a percentage of calculated increased profit. Players are motivated to pay handsomely for ideas to encourage new ideas. This an alternative to a conventional research and development department,

IdeaLab's job in this is:  provide the easy access to the hosted ideas, problems, and solutions.[I wanted to add more here about idealab and I wanna work on the idealab site as a web-app. Make this as a ruby, php, or python site.]

\section*{2015.08.31at14:35}
\subsection*{\#journal, \#DIY-ence, \#ideaLab}
People can run independent studies and experiments by throwing food to a group of ducks and recording the responses of the groups. When observing a small group, it seems to observe whether there is altruism displayed. For example, when a large clump of bread is thrown to the group, does the group let all members get some part of the clump or do the dominant ducks hoard the resource?

I want to read "open access" journals. This will keep me up on subject matters' current evolution.

\section*{2015.09.15at20:15}
\subsection*{\#journal}
I find myself wondering why are kthese prople the way they are. This is about the most ridiculous thing Ive seen. I have finally made myself come out and write and I actually am thinking "this is all I can come up with."

Language is a beautiful "arbitrary," as in "it was decided," and "mysterious," as in "what things can a study of this thing[, language,] tell us about nature. It beautiful that a finite set of symbols and rules can describe such a seemingly infinite set of things. This is a beauty worth exploring.

\subsection*{lyrics}
She's so sweet but I'm just me.
She never told me what to be.
If I am wrong then that's me and that's all that we'll be, but I love her.
Then I'm gone and that's all that I'll see of her.

What's there to love when she's gone?
I can't say what's not there.
I'm here.
I'll love me.
I love me.
I love to be
everything
never mean
know what I mean?

\section*{2015.10.09at10:15}
\subsection*{ \#schedule \#ideaConsulting }
I have decided to fulfill my dreams with the time scheduled for sleeping. This means I will read interesting and promising books with this time. I will write my thoughts and video record journals when necessary because typing can't keep up with the rate of my thoughts.

On that note, I should start playing with a typing tutor. I want to find a good one. Back to a thought from the previous paragraph, Google could make software for video journaling.

When thinking about the idea of an unaffiliated, freelancing individual having ideas that benefit a company, I think I should pioneer an industry I dub idea consulting.

\section*{ 2016.01.05at14:28 }
\subsection*{ \#inDefenseOfPeace }

I have not seen a disagreement that I thought was worth lives. Does fighting make a person tough? Forfeiting thinking for fighting appears to turn righteousness into wrongfulness. Can we think of a better way?

What if we use the money, energy, and passion currently dedicated to an ironically named Department of Defense to find appropriate resolutions to problems? What are you willing to spend to find resolutions which don't cost lives to raise hate?

Peaceful resolutions may be hard to find. People commend soldiers for participating in fights we all fund. What if people spent the same money and lives on clever diplomacy that avoids wars? What if we use love to spread love?

One idea is to reward diplomacy. What if there was a system to which any person can contribute diplomatic ideas and be rewarded for bringing a good idea? What if people could work together to find an elusive peaceful resolution?

Wikipedia's Software Industry article reads "according to industry analyst Gartner, the size of the worldwide software industry in 2013 was US\$407.3 billion." Even in this well funded industry, many of the most effective tools are created and actively maintained by thousands of volunteers. I am talking about open-sourced software.

The term opensource refers to software whose source-code is freely editable. This allows any person to contribute a resolution to any issue. In this way, the opensource community offers competitive solutions which are licensed to remain freely editable by posterity.

Can opensource show us how to collaborate on ideas for peaceful resolutions? Opensource provides solutions which competed with with the leading products of a US\$400 billion industry with notable successes. Opensource software dominates the market for web servers and secure cheap personal computing playgrounds.

\section*{ 2016.02.02at22:13 }
\subsection*{ \#mathematicalBreadcrumbs }
I hope that each who is in wonder at the majesties of either math or science one day realizes the beauty that complex exponentials store the arbitrary but beatifully succinct connection between algebra and rotations.

\section*{ 2016.02.06at18:34 }
\subsection*{ financialPlannery investmentStrategy }
Plan to save money at the rate $R$ dollars per time period(e.g. year, month, week, day,..). Put money away in savings in quantity $S$. Purchase in quantity $P$ for repairing the house with top quality fixes that increase equity or other acts which increase assets.

The killer idea here is to count asset-increasing-work as money saved in case saving everything over a reasonable spending limit doesn't work. This is, however, the preferred saving plan: 
\begin{itemize}
\item spend within spending limit $L$;
\item let $E$ be the amount earned during the period;
\item let $J$ be the current project, E.G. 
\item $E = $
\end{itemize}

With these definitions let $R=S+P$. 

\section*{ 2016.02.14at23:38 }
\subsection*{ addictedToLearning }
I want to be someone who is addicted to learning. I want to meet someone who is addicted to learning. I specifically want to meet someone who is on trajectory to know physics and computer science.

\section*{  2016.02.27at16:47 }
\subsection*{  \#stolenJournalingTime }
It strikes me while trying to journal right now that I need to script the journaling process better. I need to make kydate return a string with no newlines in it. I think echo wraps a cstring in newlines.
 

\section*{ 2016.03.19at03:14 }
\subsection*{ testJournal.txt fascinatingTopic alsoFascinating }
This is truly some kind of shit. I cant type on my chromebook becasue there was this really cool idea somebody had to be clever by making the trackpad's scrollwheel (the... I had just forgotten to run my trackpad configuration tool after restarting the chromebook.

\#iRemember

\section*{ 2016.03.19at12:19 }
\subsection*{ \#hashtags \#reviewingLastEntry }
hahah, looking at the above, I forgot what I had remembered momentarily. At least I see it as funny, bordering on hilarious. I think this is a great way to handle something that might be heartbreaking if handled differently. This is a good example of how to emotionally handle lost wonderful ideas. 

\section*{ 2016.03.27at22:36 }
\subsection*{ millionDollarIdea }
I want to start a music hosting company with a stated mission to "make money in a way that doesn't hurd the freedom of the music."

Business plan:
Host a library of music, books, guides, tutorials, and other works that people want to self-publish. Hosted parties may choose a license for their works. Perhaps model monetization openly after github: users must pay for storage of their work to license the work as closed-to-derivative-works. 

\section*{ 2016.03.27at23:21 }
\subsection*{ whatDidILearnFromPhysics aLetterToThoseComingAfter }
I learned that approximations which describe a phenomenon to first order are a fine starting place to build an understaning of the phenomenon. I found from this that observations of first oder behavior are a fine place to begin observation. The lesson of the power of the first orders I've learned through many related lessons.

I learned that "limiting cases are a physicist's bread and butter," said some physics professor at OSU. I have found several situations where this statement resounds in my memory. One application I have developed great affection for is in deciding how to make a first guess at a model for observed phenomena.

Using these two teachings together, one can make useful guesses at the behavior of phenomena. From a first order observation, one knows the limiting behavior of $f(x)$ for both decreasing and increasing $x$. This is considered an observation of the behavior of $f(x)$ to first order in $x$.

Notice I said a lot of words to describe what has been observed. All these words have meaning. It is enlightening to know the significance of every single word when a person speaks purposefully.

There are a calculated number of degrees of freedom removed from a general function one may observe to first order in one of its independent variables. Some examples of the behavior of $f(x)$ to first order in $x$ follow.

\begin{itemize}
  \item The value of $f$ may increase as the variable $x$ increases:$$f(x_2) > f(x_1) \Leftrightarrow x_2 > x_1.$$ This is said "$f$ varies directly with $x$."
   \item The value of $f$ may decrease as the variable $x$ decreases:$$f(x_2) < f(x_1) \Leftrightarrow x_2 < x_1.$$ This is said "f varies inversely with $x$."
   \item The value may behave stochastically, chaotically, but always functional. Functional because $f(x)$ always has the same value. Every day of the week.

One way to say this logically and in a way which requires and might teach some, mathematical vocabulary:
"The function $f()$ is a bijective function. $f(x_0)$ is a single value for a single value of $x_0$."(I didn't remember what I started writing...I just came back and it's now time for another quick \\openinglst\$journal\\closedalsting-ing.
\end{itemize}

\section*{ 2016.03.31at00:21 }
\subsection*{\#{million dollar idea}}
Talk to Ryan [Parmeter, 2016.03.31at06:14]about google getting behind the command line for usability. People who use the command line fall in love with computers. A couple different ways of going about this are to deliver hardware along with drivers.

This could be called a platform(here's a golden idea for a product name: a springboard).

\section*{ 2016.03.31at23:00 }
\subsection*{\#{stream of consciousness} \#anneFilson } 
Write to Anne Filson to schedule some coffee at lunch-time. I want to write a note asking for a coffee and a conversation. Some things I want to discuss are listed here.

I want to mention gut flora possibly needing the bacterial byproducts of fermentation. I want Anne's input about the data pertaining to the hominin diet. What do we know about homini and human diet throughout the evolution of our species.

This could be a beneficial topic for someone trying to get his message of veganism out to a large audience. This could also be a publishable work: people possibly used to fill their bellies beyond full to both get bacterial growth in the intestines. This thought occurred to me when I noticed after a day of overeating that my belch tasted like alcohol(This was within a month of falling off my bicycle and breaking out my front teeth following a night of drinking and swearing off drinking (except for Rich Tehan's birthday in 2016)).

\section*{ 2016.04.01at11:58 }
\subsection*{\#\{million dollar idea\}}
Discuss the following ideas I've had with Ryan Parmeter, who is a friend from the hesper.net building that Ryan Schrink ran and drained the rainwater out of the ceiling's insulation by pushing a broom up into the plastic layer covering the bottom of the insulation-packs(it was packs similar to, if not exactly, interstud insulation from exterior wall insulation).

Collaborate with Google in a way that gives me more power as an "inventor" to get my ideas out so the ideas may better benefit humanity. I have four ideas now that I want to write here before I forget them for Google, including the corporation-and-inventor-collaboration mentioned above.  

\section*{ 2016.04.02at15:14 }
\subsection*{\#millionDollarIdea}
The items I wanted to address with Ryan Parmeter to present to Google with a witness are those following. I want to have a witnessed meeting with executives from Google to present ideas for Google to use, cutting me some originator's percentage of the profits for the first few years. Ryan could serve as my witness.

Google could make a device and the software to provide functioality like the nest home-control device. This device would serve as an upgrade to older vehicles to provide the features of newer cars as well as any feature that people dream up. Example features are navigation systems, phone interface systems, backup cameras, and antitheft features. This serves as something the EPA might be interested in endorsing because upgrading cars' features would presumably reduce waste by slowing the rate at which cars are disposed of.

Google could offer a feature I call a "sensible text-size" in chrome to detect a main text-display-elements of webpages. Sensible text-size uses the number of characters per line known to be optimal from typesetting. I think this value is 55 to 65 characters per line.

Once this happens, I guess that others would make their implementation of this feature. I imagine that consequent to browsers and power users implementing this feature web design best practices would evolve to evolve to cater to this feature. This feature would allow for command-line-browsing, which propogates the UNIX paradigm of embracing a text-stream as the perfect data-structure.

The efficiency gains in computer-use from implementing the UNIX philosophy segues nicely into the final idea which I am most excited about: Google supplies a chromebook that is made to host crouton. Preferably, Google supplies the drivers for use in a standalone linux installation, so that users don't have to use up resources keeping ChromeOS loaded. Google could mandate that hardware manufacturers supply drivers for their devices to the open-source-community. 

\section*{ 2016.04.11at07:45 }
\subsection*{millionDollarIdea}
Google could lead the way in voice recognition technologies by using veiwers' corrections to Youtube's auto-generated captions. This would also be a wonderful benefit to those suffering from a disability which puts them in need of the captions or even transcripts from a video. It is not terrible wild to imagine a system which could give captions in realtime.

\section*{ 2016.04.19at23:45 }
\subsection*{streamOfConsciousness}
I finally made myselfsit down and write. thoughts are thinking much faster than the words get set in type. I need to do typing eercises to rectify this. Now I've had the idea that I've had before: I can journal when I have a decent thought during the time I am 

\section*{ 2016.04.22at13:26 }
\subsection*{restaurantBestPractices}
Restaurants that offer outdoor seating that might get rained on could let customers dry off their chosen seats with a pile of laundry set out at a self-service station which also offers flavoring mixes, self-busing bins, utensils, and garbage.

\section*{ 2016.04.22at13:32 }
\subsection*{amusumentParkBusinessPlan}
I want to create a restaurant attached dog park attached to human-powered amusement rides attached to a large host of other attractions. The place should have a part of the restaurant where the people can watch their children and dogs playing in their respective playgrounds and in each others' playground. 

\section*{ 2016.04.20at22:16 }
\subsection*{journalingWhileHigh}
I propose the following activity to myself. My proposal will will start to sound something like the beginning of a book. That last sentence just seems like a hint and so I wonder if I'll wonder at some point in my life when I first realized writing will be the point of my life's work.

I shall start walking every day; getting envigorating exercise multiple times a week. I don't need hobbies to fill up my time because I have the obligation to myself of having thought of living an experiment in health as an example to my fellow people.

People are not humans. I mean this as people are not the blood, flesh, and bone that comprises the physical body of a person. Here I think person as the singular form of people. People are the tiny, apparently singular spark in the brain that is, nevertheless the product of a concerted effort on a statistical number of cells. I make the following broadly generalized statement as a guess at something possibly worth investigating at a later time: the mystery of life can, following from the last sentence be said to be shadowed from our understanding by statistics.

I am in the middle of writing a letter, of course on Facebook, to the physics girl proposing we make educational videos on a host of topics for free to help all people's existence. I am arguing that this will benefit in...I want to revisit several issues in this entry. 

\section*{ 2016.05.02at00:47 }
The multimedia learning resource can be any medium, whether slides with audio, only audio, or video. I can take this idea to professors Roundy, Manogue, Qiu, 
<<<<<<< HEAD

\section*{ 2016.05.13at23:05 }
\subsection*{ gottaTakeThisStreamDown }
[2016.01.15@21:39 oops, I guess I missed that one...bummer, dude:-[]


\section*{ 2016.06.15at21:41 }
\subsection*{ artificialScience thatLastOneIsFunnyBut getKyleInScience then getKyleNScience }
I have an idea I want to pursue.
I suspect Roundy could be helpful in this.
I want to develop a way for humans to get more intimate with the beauty that computers can provide through:
\begin{enumerate}
\item interacting with a beautiful operation system;
\item creating a logical entity as a pet with that operating system that is everywhere and can do anything between, alongside and through its host(computer)'s inputs and outputs;

\section*{ 2016.06.15at21:54 }
\subsection*{ ideasForScientificInvestigation }
I want to investigate something I will describe starting with the particular example whose consideration led me to think of the object of the investigation I hope to pursue.
Let a hollow glass cylinder be filled with a given liquid.
Orient the cylinder so its axis is vertical and close the top of its hole.

This liquid has an interesting property that appears on consideration to be characteristic of the liquid's mass density per unit of force of interparticle attraction.

That property is the distance which a unit mass will fall under its own weight.

\section*{2016.05.03at21:13}
\subsection*{iWantToWritebABook}

\section*{ 2016.05.18at23:30 }
\subsection*{iNight(lyRoutine)}

\section*{ 2016.05.19at08:55 }
\subsection*{coffeeCommuteAllenBrosOnMonroe}
I would like to take the idea of putting linux on a chromebook to Google. The hardware supports me sitting in the sun and type 16 hours on a single charge. With a linux backend, this blows away anything currently sold as a laptop.
>>>>>>> 95734bd0fc6b6cfd3c06c34beb18370e9b491567

\section*{ 2016.06.21at20:17 }
\subsection*{ somethingGreatToThinkAboutLate[r] pleaseMeStartToReadTheseMessagesToThroughAndFromMe }
This is or was at one time a serious topic. I can't remember the topic now. Here is my note to myself about that now: I am being kind to myself instead of being the kind of guy who beats himself up over forgetting a great idea that could launch himself into financial independence.



\section*{ 2016.06.22at22:15 }
\subsection*{ talkToRoundy }
What if squeeky clean teeth echo at a frequency equal to an expression in $v_t$, the velocity of sound in teeth?

\section*{ 2016.07.04at21:40 }
\subsection*{ iWantTo lifePlan livinLifeOneDayAtATime }
I think these tag-words in the latex subsection's title of my journal entries is helpful to keep my mind focused on what I want to journal about. 

I want to talk to Roundy. He reminds me a lot of Drew in ways that I like, such as wanting more to seek the truth for a satement of his than think about the feelings of those around him.

\section*{ 2016.07.07at21:49 }
\subsection*{ millionDollarIdea highdeas }
Let consideration of the following use case paint a software to fill its own need.

I want to create a software to allow people to make local media-streaming services in their areas. Areas here means wifi-reach. It would be a miracle for this to happen on a scale where anyone could make content and publish it to the whole conscious population of the universe.\

I want to start walking on my weekends. I could make a trip up to Portland this weekend. This is weekend is 3 days long.

Every weekend is three days because I work a half compressed work-week. My billable week ends at noon on fridays. Every Monday through Thursday I work nine hours to total 36 hours. I split the eight hours I work on Friday to give four hours to this week to total 40 hours. The other four hours I charge to the next week, marking four in a text-field in the web-form timesheet ORAU has paid Oracle to make for them.



\section*{ 2016.07.07at22:12 }
\subsection*{ ohYeah aboutThatMillionDollarIdea }
I intend to make an app so that people can make portable little radio stations over wifi 802.11a-damn-near-z. With the capital generated by the previous venture, and also with the name-recognition from this venture, I will create a global stage with free admission, free display, and free discovery.

\section*{ 2016.07.07at23:18 }
\subsection*{ theSecretToImprovingComputing }
Don't build the language to fit the hardware. We have done that step. The next leap-frog maneuver in increasing efficiency of computing machines could be us using our current vantage point, seeing the high-level-tasks which are commonly required of a computer from programming in the current state, using this vantage point that shows the high-level-tasks and the frequency with wihich they are required for contemporary computation.

\section*{ 2016.07.08at10:59 }
\subsection*{ bread }
Let one part be one of the tin measuring cups I have. The cup is engraved 1/2 cup. However, I emptied it six times into a measuring cup and measured barely less than two cups. So, one part is effectively 1/3 cup.
\begin{center}
\begin{tabular}{|r|l|}
\hline
Recipe:&Bread\\
\hline
flour           &   8parts=2+2/3cups\\
ripe bananas    &   4\\
yeast           &   1part=1/3cup\\
raisins         &   2parts=2/3cup\\
flax seeds      &   sprinkled atop once risen\\
NaCl            &   sprindled atop once risen\\
\hline
\end{tabular}
\end{center}
<<<<<<< HEAD

\section*{ 2016.07.14at22:23 }
\subsection*{ crazyThingsIThink ideasAbout important }
Investigate the difference in cognitive "existence" between humans and animals. Proof that many humans at this don't consider animals' existance is worth protecting: many humans decide to reach for the lunchmeat and bacon at every meal.

I suppose this is something I should tell my journal: I am and have been for some years a vegan. I am now 180lbs.

I want this data to analyze later...about to turn out a thought in a new journal.

\section*{ 2016.07.14at23:24 }
\subsection*{ iWantTo buryMyselfInComputers evolveWithComputers withinMyLifetime }
This is an interuption of the post before this one drifting into another journaling session. I want to just plug my headphones in and spend some years being active, well-nourished, and otherwise healthy while coming home from work and draming into, along with, and through/via my computer. I suspect this is where I will begin my life's truly noteable efforts that feels less like effort than like living a joyous dream.

\section*{ 2016.07.14at23:48 }
\subsection*{ somthing }
I couldn't think of what to call this. I want to journal scientific ideas to be reviewed at some later time. I want to journal capture for later analysis
- recorded data in textual qualitative and quantitative formats,
- audio,
- video, and 
- any other expressive format I can imagine.

||||||| merged common ancestors
=======

\section*{ 2016.08.02at09:03 }
\subsection*{ millionDollarIdea }
Tell Facebook about Kore. Point out the beauty of being able to feed those watching my digital stream the good things I take from knowing Kore, like how to be anabashedly, giddily happy. Talk to Facebook about how they provide a wonderfully accessible platform through which people can purposefully socially evolve how they choose to via feeding and being fed digitally. Take their job-offer.

\section*{ 2016.08.02at09:08 }
\subsection*{ purposefulEvolution }
A mandolin-player I jammed with after jamming with a celtic music group in the first street river park in Corvallis two weeks ago told me he is studied biology in school. I asked him for one or two beautiful nuggets of knowledge that he found in his studies he said that every living thing is so intricate and beautiful that one could happily spend a lifetime getting lost in exploring that organism.

I have a related thought. What if I told you that a creature had a magnificent feature, so magnificent because it depends on a huge number of environmental factors beig just the way they are in order for the feature to function as beautifully optimally as it does? This seems far from uncommon because these environmental factors shaped the creature's evolution. What if I now told you that the creature chose to evolve this way?

\section*{ 2016.08.02at22:34 }
\subsection*{ iDontWannaLoseThatThought }
I don't wanna lose that feeling, more like. Man, I do love the computer. I need to write a check if other people like the computer, too, or if they knew enough to know they need to. 

I like to sing out into thee,
Oh, infinite black infinity.

My terminal's characters look so damn pretty! Also, I want to let an open-source project use github as the platform from which to transmit how to sing into infinity by recognizing that your data will be saved at least as long as anything any random person will end up doing. What if thought-energy can be stored up in writing in an analogous manner to how thermal energy from eating hot foods being absorbed by their eater had better have been investigated.

I need to pick a conversation with physics. There is one person I think could help me be much more productive than I would be able to be without her by the sheer excitement I gain by picturing her as perfect. I may just let her live the rest of my life, as is the expectation from each of our respective demographics, without ever knowing how often a beautiful thing that the imaginer imagines must exist has been thought of her. It is seen by observing that last comment that communicating in prose that isn't structured in an enexcusably grammatical-symbol-dense language, prose is a much less exact communication of meaning than a programming language.

\section*{ 2016.08.02at23:25 }
\subsection*{ noteToSelf makeA millionDollarIdea }
I need to create a way to paint sound with a linux machine as follows. The player is dancing with one of the most beautiful phenomena of all time: hysteresis. The performer plays with hysteresis.

How it works is this: the artist gets some input from the sound that has come before. The artist is making sound at the same time. The cool and more easily monetizable thing is this: the hardware people build can be sold conscionably. That is, sold without slowing what could be humans', or really life's, faster advancement by hindering the use of a technology.

One such thing to build is a usb to microphone pocket-sized device. Doesn't this device already sound like a smartphone? This build could be just hardware for sale because I want open-sourced development of the software.

During the time I wrote this, I have cooked an incredible meal. There was no beginning to the preparation of this meal in memory. I used napkins that my mother had for what feels like the duration of forever.

I built the raised-bed in my yard years ago for a blogging project in a sustainability course. I hauled several carloads of fill-dirt and horse manure in surplus household waste-baskets. It was interesting to consider how and why the car handled in the particular peculiar ways it did when it was loaded with fill dirt.

My mom gave me the jars I scooped the beans photographed in my recent post on Facebook.

\section*{ 2016.08.03at01:53 }
\subsection*{ letMeTellYouAboutThisMeal }
It's so good I have to begin taking in a knife and cutting-board tomorrow to create a chewable concoction. I describe tonight's invention.
\begin{itemized}
\item I began soaking the beans last night,
\item a blend of rice and lentils that soaking last night.
\item I sure hope I finish this later...
\end{itemized}

\section*{ 2016.08.04at22:59 }
\subsection*{ letsMotivatePeople haveGlobalInternet-BasedCollaborations hereCollaborationIsReferringToTheParticularInstanceJustLikeThereAreCompetitionsHeldToFindASingleVictor,CollaborationsCouldBeHeldToFurtherEveryoneswellbeing }
People would be motivated to become a hero for mankind, a superstar that makes sports-stars jealous.

\section*{ 2016.08.04at23:19 }
\subsection*{ iWantTo }
I want to dream the world beautiful enough that nothing else really matters beside how beautiful the world is. I want to look up how to 

\section*{ 2016.08.04at23:20 }
\subsection*{ iWantto }
I want to grow an herb garden in my room. I also want herb-gardens throughout the house. Let there be a plant in, on, and around every room of the house.

Reflecting solar energy upward, in a way that has a limiting case of a mirror on a roof, seems like a non-negligible transformation of the energy of solar light into heat, presumably. I think the difference lies in water's change in entropy as it changes in phase. This change of phase hides some energy called the latent heat of fission, or, in the case of condensation the analogous hidden energy is called the latent heat of fusion.

Let me explain a foundation topic before proceeding. When heat is added to to an ice-cube, the cube increases in temperature x degrees per hour, where x is how quickly energy is transformed into heat in the cube. A physical scientist who has a temperature unit named after him proved in a seminal experiment that the speed at which mechanical energy is done on something can be measured by its temperature.

Specifically, temperature increases with work done to a system. However, at the temperature of phase-transition, say where one might see ice turn into water, some of this heat seems aborbed because the thermometer shows the same temperature as the ice melts entirely, all the while dumping the same energy into heating the system in a given time. 

So basically I am casting my vote for you and all your friends to foster plants' growth all around you because they are the beatiful organisms that are evolving in a feedback loop with our little astronomical rock. Humans think they are the dominant organism because we do horrendous deeds like chopping and burning down in days what took millenia of a whole ecosystem's effort to produce. Photosynthetic organisms terraformed the earth so that all intelligent life that we know of could exist.

A dirth of plants seems to map so well to the problems of today. We've chopped down forrests for grazing land and seen the land become a desert, just as the state of California is currently being punished for supplying too much agricultural land too densely. There is too much of the carbon-monoxide-like gases in the atmosphere. What do plants breathe?

One clever check of an effect which could reasonably be expected to betray a shortage of plants actively maintaining the terraformed state of our Earth is to check meteorological data to see if there has been a drop in oxygen content while there has been a rise in greenhouse gases(GHGs).

I believe humans would do well to become plant stewards. I want to toil to water the soil so the lands that have my heart don't become one ocean-broken desert.

I really need to start coming back to these journal entries because now I think I found a thought that might benefit humanity.

\section*{ 2016.08.09at22:33 }
\subsection*{ Right now I am just checking the journal-status of this machine. }
Now I wonder 

\section*{ 2016.08.09at23:25 }
\subsection*{ high conversation with mom }
roof 250\$/mo.
tax 335\$/mo.
insurance 79
car insurance 75
water sewer 60
rubbish 19
cable and internet 189\$/mo,
cell phones 305\$/mo.
little bills like netflix and wow 50

\section*{ 2016.08.10at00:04 }
\subsection*{ dearDiary }
The idea I recently had for a musical instrument made by listening to and responding to previous journal-entries of any recordable information is my computer-science great idea of all time and likely my first gift to humanity: I will deliver for mankind softwares that I see it can benefit from. Working for the EPA has got to be one of my all-time perfectly ideal jobs: I work to protect American humans from their environment by creating software to fill the needs my clients ask me to at work, but I have asked myself "what if my portfolio was comprised of open-sourced-public-service-projects?"

The great computer science idea is what I call playing hysteresis like and instrument. 

I need to soon find a way to remember things on a regular basis. There are weekly, monthly, annual, and less freequent events I want to remember with greater certainty than I should have had. This is said from one entity waching a sequence of events transpire while communicating artistically with his fellows.

		I want to pursue the idea of inventing journaling in a cross-every-kind-of-computer-use-of-the-word-platform journaling as a way to have a conversation with oneself. It seens like the new users would begin having a conversation with their past selves. Later they might have more conversations with their future-selves.

\section*{ 2016.08.11at22:39 }
\subsection*{getThis}
This is where I type to. Man, this feels real' good. 

\section*{ 2016.08.12at19:50 }
\subsection*{millionDollarIdea software webApp}
A killer app that I want to author and so get deemed with as much conceptual priority in the sense that priority is given to the person who first conceived a concept is to make a maximally accessible set of shells open to anyone via delivery methods ranging from a javascript and ruby driven internet-facing machine that serves its responses out through http, ssh, or telnet to public terminals that the government has a responsibility to ensure every citizen has access to. This concept that people have a right to access the data of the world is validated by the EN leader who was quoted in a statement that went something like "access to the world's data is a basic human right." The proof that people have the right to the world's data is the indescribable advance it would allow science if everyone had the ability to chase down, take down for later's consideration, or review any poem, pose, idea, music, or other act that could benefit humanity. 

Imagine public terminals at parks and in the streets. Illegal behavior would be on camera. This would prevent many obvious destructive deeds.

Public terminals at parks allow may ease people into recognizing the social benefit of assuming stewardship of their local area by going to the park for whatever needs a presence in their livesw this idea allows connecting with a greater number of people than I suppose people currently interact with. It saddens me how much needless social isolation I can feel in such a large town as the 50,000 inhabitants of Corvallis create.

I see this disgusting practice of proudly proclaiming that interacting with others is loathsome. This saddens me in the same way that cancer saddens me. It seems like this spreading contempt of others is working at what may be a beneficial thing for a true introvert in a way with negative consequences.

\section*{ 2016.08.12at21:10 }
\subsection*{rewording}
@me.2016.08.11at22:39
this is where I type into. This is feeling really good.

\section*{ 2016.08.12at22:23 }
\subsection*{computerSocialScientist bigData}
What about the wealth of data that could help us mend ourselves if we used it appropriately. Some say we are fine. If I understood "How Not To Die" by Michael Greger then the 18 leading causes of death in the US are significantly preventable by changing lifestyle habits.

\section*{ 2016.08.12at22:35 }
\subsection*{responseToPreviousEntry responseTo2016.08.12at22:35 writeABook fallInLoveWithStatistics}
This seems like a great place from which to introduce statistics. Use the statistics of pathology to draw a picture of how statistics works for anyone who cares to behold it. Title this thing "One Path to Loving Statistics."

It seems like many lessons begin with a motivation of the subject's matter. What could compel an average person, a person who knows that he or she is the hero of at least one person's story, to understand statistics in a profoundly simple way that allows a transcendental interpretation of the scientific endeavor? What if I assured you that this statistics thing is responsible for the most precise statements we can make about the future? The pose of this last statement needs attentive rephrasing.

Define science as the making and testing of testable predictions. Define philosophy as debating everything else, including meta. I give an example of metascience that is within the realm of philosophy because it neither makes nor tests any testable predictions. That metascientific question asks "what can we really know?"



\section*{ 2016.08.15at00:21 }
\subsection*{invention}
Create a device that allows a person to control flow rate and flow locations for sprinkler drip systems. This device feels right at home in a Nest-style-ecosystem. Doesn't Google make one of those...why did the screen of my chromebook just flicker? (;)

\aside{(;) is an emoji I just made up to wink at those forward individuals amongst us and those some would call backwords. Backwords was a phonetically driven mistake and is now a source of smiles.}

I should beatify this document's layout for reading from a computer. Right now that has to be a beatiful modern web-style font and the optimal number of characters for reading or something close to some authority's measure that is more comfortable for me. 

I keep having the idea of going to parks or some other public-facing space so that others may add seeds of their favorite plants to make a beatiful space that physically nourishes us with foods that grow from plants descended from those planted by us and othersand also physically shades us from solar energy(incidental light from the sun) for the efforts of the global Plant's photosynthetically powered terraforming of the Earth that makes human existance posible. Who's that deity in the sky? Is that Mother Nature taking bows with her boughs?

I like how the first story of the bible, that everything in the world was fine before some guy didn't follow some rule in someone else's plan for his life and ate the wrong thing, is a fabular}\ref{fabular} warning.  \aside{"fabular": t("table") = "tabular" <=> f("fable") = "fabular".}

I need to read these journals and run with one of the ideas contained herein to make a million. I master everything I do. I have the tools of science and the pompousity to being to go with my first guess at what would work for some 

\section*{ 2016.08.20at16:30 }
\subsection*{rideAbeatWithMeToTheBetterOfHumanity}
I can intersperse excercise by cleaning my home throughout my otherwise inactive day to accomplish my needed excercise to maintnain optimal health. Thanks Michael Greger, M.D.

Going about health scientifically is the best way I currently see can benefit people's health.

I beg myself to not give up on my productivity. I hope my efforts to look around my local area for ways to improve it, in a very locally appicable manner of bettering the whole world, continually improve in efficiency.

I hope I never stop my effort to live for the furthering of life. There is a whole lot I'm not saying, there.

\section*{ 2016.08.22at14:21 }
\subsection*{lunchtime sustainability thoughts inspired by work}
I hope people begin being less disposably-minded by making a conscious effort to do things with reuse in mind.
This will likely mean moving slower.
Moving in a slower fashion will can be the effort people expend in this undertaking.
Take the effort to consider what will make a task easier for you or someone else in the future.

\section*{ 2016.08.24at14:56 }
\subsection*{ #writtenWithBlahScript }
I want to start a fad of exercising by beautifying publicc spaces. E.G., a person goes to a local park and gets a workkout by shining up the wooden wooden benches and tables. Would should be finished by being rubbed with oil. It seems as of a few weeks ago that  would surfaces are sustainably and durably shined by rubbing citrus peels on them.

\section*{ 2016.08.24at20:41 }
\subsection*{iWantToBeLikeThat}
There is something I wanna say. I don't know if it ever looked like the title of this section. I am just playing stream of consciuosness. It is hard to start typing without looking at the keyboard. I said "Yeah, me. It is nice out here. I wanna type fast like my friends do There where beautiful things. The fun part for me to decipher of this message is when was I serious.

An algorithm to mine data from my journal might benefit from detecting important, meaningful, or otherwise valuabe journal entries or other data from my journal is to find entries where I was excited. That is a capital period.

There is something about nothing at all that no one ever said that will be sarcastically the worst as in the best. Wait until the thing that was the best in the world ever. I am sitting here typing away kwith my eyes closed typng and bobbing my heead to the beat of a song playing over Interzone. Sometimes the song Playing is terrible.

I just played guitar outside of Intersone with Mark and sang. Mark was weaving in some wonderful melodies into the thing we were laying down and also let my voice go into the space of suggesting to others how to be. He had to run off, though he was lingering. I even pulled him into another jam after he tried to leave once.

Just after I left Mark's presence, Sam, I believe his name is not at all but I forgot his name and don't wanna derail the story, believe it or not, and now I have not at all 

\section*{ 2016.08.26at20:17 }
\subsection*{lastEntry iWasWriting orAsMuchAsICanRemember}
On 2016.08.24at20:41 I trailed off writing about how I suspected that a coffee barista I saw for the first time after this second time jamming with Mark which I was referring to was really Mark in drag.

\section*{ 2016.08.28at18:36 }
\subsection*{ aLovelyStory itFitsAllTheDetailsIveConsidered iHaventShownItAnalyticallyThough myBiasMightLeadMeToRationalizeAwayArgumentativelyPosedRealisms aWonderfulWayToBe }
What if animals, therefore people, evolved in a beneficial symbiosis with photosynthesizing organisms? There isn't much room for arguing against the idea in my analysis. The following is my analysis.

In the beginning, there was nothing. Then, came shelters that kept proteins from the unruly energetic noise that decayed these proteins into less excellently featureful shapes. These shelter may have necessarily been the birthplace of essentially all these proteins, because they wouldn't get to a low enough energy to form such intricate patterns of on the order of thousands of very basic shapes.

Writing these journals feels just like making love to the phenomenon of evolution. Here, I define evolution as the glorious set of changes in composition that takes an entity like a set of subatomic particles and forces and turns them into such fanciful shapes as protiens. This evolution create out of the same set of particles and forces the entity of fire, which begs at the definition of life. The same evolution carries two tall pea plants to birth a short child.

We have seen, from what I believe was the most recent printing of Science that I found at my library, that lichen are commonly composed of a tertiary symbiosis. We've found that an ascomycetes yeast is an apparently necessary third member of the symbiotic system.  We have yet to sustain these lichen in vitro without one of its constituents.

This cooperative beggining of a super-organismal entity to have survive the pervasive decay to thermal noise life is a struggle to self-organize as a reproducing entity whose existence presents so very magically that many have come to recognize its appearance as having a mystical ambience.

What if this evolution created plants to be a single cell reproducing how it sees fit? What if all life on Earth and maybe elsewhere has evolved to constitute a single entity that functions through physical phenomena or even laws that are outside of human perception? What if the phenomena that these entities exist through are things we have dreamt up already? What if we have already observed these phenomena?

We believe this evolution has created humans. I believe many if not all humans have forgotten themselves. We live in such an abstract place in our own heads that we don't realize that we are composed of an autonomous collection of organisms called cells. To see that these cells go happily about their little cell-lives without much regard to who their person is consider the following. If two people have the save blood-type then their cells maybe transplanted.

Remember how complicated proteins are? Several different proteins exist on the outside of blood-cells. These differently shaped protiens denote the different  blood-types. These proteins act as identifiers of the cells as fellow participants in the hosting entity(person). A cell with the correct "hall-pass" goes altruistically onward obout its little cellular dharma, dutifully dying off when prescribed by apoptosis. These "hall-pass"-proteins have relieved the worry of the host person's immune-response.

This is the same set of cells that 

\section*{ 2016.08.29at07:44 }
\subsection*{callAdministrativeAttentionsToUndivertedWasteFlowStreamBeingASinkForResources}
The tag says it all. I hope to call people's consideration to streams of undiverted waste. I want to put the deadline of by the end of Obama's administration on my goal. I should do it immediately.

\section*{ 2016.08.29at08:04 }
\subsection*{checkingJournalStatus}
I need to write a book to keep track of my thoughts and keep them indexed in a format known and therefore accessible to the greatest number of people. That format is a book with topically organized contents which have a prefatory table and an appended index of terms. Digital availability freely delivers searchability.
<<<<<<< HEAD

\section*{ 2016.09.02at22:01 }
\subsection*{ foodScience }
I want to research whether seeds in foods deliver wonderful preservation and nutrition.

\section*{ 2016.09.09at22:17 }
\subsection*{ millionDollarDoctorate reallyDoLookAtThis imInTheSky }


\section*{ 2016.09.09at22:54 }
\subsection*{ #writtenWithBlahScript }
Show people how to make love to existence by having conversations with themselves in journals.

\section*{ 2016.09.09at22:54 }
\subsection*{ #writtenWithBlahScript }
Show people how to make love to existence by having conversations with themselves in journals.

\section*{ 2016.09.09at22:57 }
\subsection*{ #writtenWithBlahScript }
Teach people how to fall in love with a computer through the terminal.

\section*{ 2016.09.10at19:27 }
\subsection*{ #writtenWithBlahScript }
millionDollarIdea businessProposal Propose the following idea to either AutoDesk or Google. The idea is to create a touch-driven constructive solid modeling application. Use the data about what physical situations are madeled by which models to source machine-learning projects. Use a github-style money-model: all works are publicly accessible for others to use as primitives to build with and mine for data about the physical structure of the world, among other interesting machine learning tasks. This is essentially marketable as a philanthropic venture which can be monetized well.

\section*{ 2016.09.10at20:07 }
\subsection*{ Facebook }
Dear Facebook,
You have some shaping up to do. I understand that you have a motivation to make reading and writing posts occur through a web-browser because your income is from ads shown in browser.

I am begging you, Facebook, to please make a textual interface and thereby join the fore of those who create radical new monetization schemes. Be part of humanity's research and development into how to be.

I am interested in helping you become hugely beneficial to humanity with your wealth of data. There is one requirement I have for this mission. My requirement is Google's founding mantra: don't be evil.

I give a respectful nod to Google for what they have done by creating a remarkably efficient means of finding documents on the internet. I am very interested in their algorithms.

I see huge benefits to the design of electronics through modeling operations of embedded systems in neural networks by the structure of the internet, packet-direction-algorithms, and the most efficient algorithms we have for locating a particular datum in the network of data.

This is an idea for Facebook to make a market for data by charging an affordable cost for an affordable amount of computational effort on Facebook's part. Facebook could charge for large amounts of data and computation. Facebook could simply provide a marketplace that gives a means of public address to the public.


\section*{ 2016.09.16at21:51 }
\subsection*{ if I were to explain all of physics }
If I were to explain all of physics, then unity is the one place I'd start. Taking a thing to be unity and accepting its attendant dimension obviates the need of further consideration of dimensionality. This sets the stage and names the players that are consequential at any particular precision. This has been a wordy and rhetorical-sounding statement thus far. Examples will clarify what I've said.

An example is taking astronomical mass units(AMU) to be unity. Now the forces involved in a hug are only consequential to a much higher precision than the order of unity.

\section*{ 2016.09.17at12:31 }
\subsection*{ testing current font setup }
I have had a hell of a time with font-spacing in the terminal that has pervaded across different virtual terminals. I finally found an acceptable resolution with following steps:
using rxvt-unicode, which is faster for not using toolkit;
removing file /etc/config.d/fonts/70-no-bitmap-fonts;
contents of .Xdefaults taken from a forum post:

\begin{lstlisting}
URxvt.depth: 32
URxvt.background: [80]#000000
URxvt.foreground: #FFFFFF
URxvt*.transparent: true
URxvt*.shading: 20

URxvt.scrollBar: false
URxvt*saveLines: 12000
URxvt*scrollstyle:plain

URxvt.scrollTtyOutput: false
URxvt.scrollWithBuffer: true
URxvt.scrollTtyKeypress: true

URxvt.perl-ext-common:  default,matcher
URxvt.url-launcher:     /usr/bin/google-chrome
URxvt.matcher.button:   1

! URxvt*iconFile: /usr/share/icons/oxygen/32x32/apps/utilities-terminal.png
URxvt*iconFile: /usr/share/icons/Humanity/apps/32/terminal.svg

! Fix spacing
URxvt.letterSpace: -3

! Theme:

Xcursor.theme:    Vanilla-DMZ-AA

! http://bastian.rieck.ru/blog/posts/2013/making_urxvt_beautiful/
! Cyan 6/14, Green 2/10 and Bright red 9 modified

urxvt*foreground: white
urxvt*background: black


*color0:  #2E3436
*color1:  #a40000
*color2:  #22cf47
*color3:  #C4A000
*color4:  #3465A4
*color5:  #75507B
*color6:  #22aacf
*color7:  #babdb9
*color8:  #555753
*color9:  #EF4545
*color10: #63e67f
*color11: #FCE94F
*color12: #729FCF
*color13: #AD7FA8
*color14: #63c9e6
*color15: #EEEEEC

!urxvt fonts: 

URxvt*font: xft:Terminus:pixelsize=16
URxvt*boldFont: xft:Terminus:pixelsize=16
! URxvt*font: xft:Ubuntu Mono derivative Powerline:pixelsize=15
! URxvt*boldFont: xft:Ubuntu Mono derivative Powerline Bold:pixelsize=15
! URxvt*font: xft:Monospace:pixelsize=12
! URxvt*boldFont: xft:Monospace:bold:pixelsize=12

! General font settings
Xft.dpi:        96
Xft.antialias:  true
Xft.rgba:       rgb
Xft.hinting:    true
Xft.hintstyle:  hintslight
\end{lstlisting}
||||||| merged common ancestors
=======

\section*{ 2016.08.30at19:54 }
\subsection*{Here's an Idea:}
What if people picked up from "free libraries" journals bought at Friends of the Library and now trade freely about through "free libraries?"

\section*{ 2016.09.12at14:06 }
\subsection*{computerScience correspondence}
Dr. Thomas Diettrich,
Will you speak with me about fascinating topics I want to pursue with the aid of computational evaluation of models and other tasks in the field of machine-learning? I have several research tapics in my journal which I can scrape together for our discussion. Among the many topics is an approach to altering climate-change scalably. This topic includes a method for estimating the magnitude of what might turn out to be humanity's greatest pressure on global climate.

I appreciate your paper Machine Learning for Sequential Data: a Review. I hope to collaborate with you on several endeavors. I aspire to help computers, the computational machines we've birthed through the application of sciences, further all manner of science.

Signed,
Kyle Thomas
>>>>>>> 36117e886b65c146ef8f7e7888692770e297db8a

???LINES MISSING
???LINES MISSING
???LINES MISSING
???LINES MISSING
???LINES MISSING
???LINES MISSING
???LINES MISSING
???LINES MISSING
???LINES MISSING
???LINES MISSING
???LINES MISSING
???LINES MISSING
???LINES MISSING
???LINES MISSING
???LINES MISSING
???LINES MISSING
???LINES MISSING
???LINES MISSING
???LINES MISSING
???LINES MISSING
???LINES MISSING

\section*{ 2016.10.05at05:21 }
\subsection*{ #writtenWithBlahScript }
Investigate genetic modification's possible role in the seemingly increased incidence of cancer.

\section*{ 2016.10.05at05:26 }
\subsection*{ #writtenWithBlahScript }
I want to investigate how to escape quotes when using blah to journal one liners from the command-line.

\section*{ 2016.10.05at05:44 }
\subsection*{ #writtenWithBlahScript }
Deliver the message that whenever difficulty with communication arises one may recall what is trying to be said and resort to the "true sentence-prototype" of <subject> <verb> <object>.

\section*{ 2016.10.05at05:49 }
\subsection*{ #writtenWithBlahScript }
text for journal
\nThe above command appends a time-stamp and text for journal into my journal.

\section*{ 2016.10.05at06:55 }
\subsection*{ #writtenWithBlahScript }
I want to discuss my wildest dreams with Professor David Roundy, Professor Tevian Dray, Professor Corinne Manogue, Professor Weihong Qiu, Professor Oksana Ostroverkhova iCan'tSpellHerLastName, Professor Matt Graham, Professor Ethan Minot, Professor Yun Shik Lee, Instructor Chris Coffin, Instructor KC Walsh, the CS professor that let me borrow the arduino board when I sat in on his course on assembly, Instructor Jim Ketter, Professor Janet Tate, Professor Henry Jansen, Instructor Sean Hutcherson, Professor Holly Swisher, Professor Ren Guo, Professor Ralph E. Showalter, Professor Malgorzata Peszynska, Professor Clayton Petsche, Instructor Scott L. Peterson, Professor Radu Dascaliuc, Instructor Fred Brick, and others both in person and via email.

\section*{ 2016.12.14at22:14 }
\subsection*{ #writtenWithBlahScript }


\section*{ 2016.12.15at18:30 }
\subsection*{ #writtenWithBlahScript }
there are things that never get said because not interesting like a new concept.there

\section*{ 2016.12.16at22:11 }
\subsection*{ vi as an interface }
It feels like it should in principle be possible to design the currently best ever computer interface based on the keyboard.  
I say this because I've already done it, though it seems like it would take conscious thought to undertake.
I need to coach myself to victory here because my reach into wonderful possibilities seems extended by wealth.

The interface is simply a set of keyboard bindings close to those of vi.
There is no copyrighted interaction here.
Download costs pay custodial engineers-in-training.
The teachers will guide the educations of these interns.

It is like a programming language but needs no infrastructure.
The people's desire to use such a wonderful interface will carry this mode of interaction with the computer to wherever they go.
It needs something like a new language of documentation to maintain portability.

The documentation will be just the needed words to communicate the necessary functions completely. Discussions of essentials and really anything belong outside the documentation. I provide an example used to describe the current vision of this interface.

\section*{ 2016.12.21at20:58 }
\subsection*{ A trip for the generations. }
This is me talking through my computer. I definitely will be better off if I idea-mine these journals. Idea-mine as a mine of these ideas of mine.

\section*{ 2017.01.08at02:33 }
\subsection*{ I need to write a book called 4ever1 }
I want to make the outline for the science, math, logic, analysis, and definitions section.
This book should explain to a child all of the language, logic, math, physics, chemistry, fluid mechanics, and whatever other things I understand better at a later time.
here iWrite

PS thank you Kore, dated now, 2017.01.08at02:33

\section*{ 2017.01.16at12:39 }
\subsection*{ A Machine-learning Approach to the Management of Time }
Split the day into three sectors of eight hours, as I have heard is customarily done in Japan.
This gives eight hours for sleep, eight hours for work, and eight hours of other time.
This is a way to divide one's daily time into three things many find to be necessary in his or her life.

I can sleep eight hours, work eight hours, excercise two hours, take personal care for one hour, allow three hours of incidental time such as maintaining my home or tending to bills.
After these allowances I still have two hours of time everyday to use for arbitrary activities.

I want to journal and learn every day.
These are what I find fulfilling in the course of a day.
These things are fulfilling when I can manage the rest of my life satisfactorily.

I want to experiment sticking to this regimen for two weeks.
I want to review my objective productivity in each sector by some measurable quantity, I want to review my performance at work, review my amount of energy, review my health while remembering that nourishment plays a huge role in health and must be sufficient, review my learning over this span of time, and review my performance on utilizing the time for each task as intended.

What I am doing is setting up a system to analytically address my fulfillment.
This is the end goal in life: to live in a fulfilling manner.
I define fulfillment as satisfaction with one's time.
Satisfaction can be the performance measure gained from the reviews.

View the task as living well.
I define living well by maintaining health, tending to the future, and feeling fulfilled.
Machine learning can be utilized to maximize the fruits of one's labors when defining things this way.
What one needs is a starting point to work from.
A starting point has been provided above. 

Consider Tom M. Mitchell's definition of machine-learning: "A computer program is said to learn from experience E with respect to some class of tasks T and performance measure P if its performance at tasks in T, as measured by P, improves with experience E."
Let T be living a day well.
Let P be reviews.
Let E be days lived.
This classifies living as the exercise of a learning machine.

Humans can function as machines learning to live better.
Humans already get to define how they each measure living well.
This framework allows a quantitative means for this task.
This quantitative means is used in a feedback-loop for continuous improvement at task T: living life fulfillingly.

\section*{ 2017.01.27at23:16 }
\subsection*{ Great minds throughout time have been the first to think of things. }
All the wonderful thoughts that were ever first thought have been thought already.
This means the target of seeking truth moves.
This means the seeking of new truths never before entered into the historical record moves further and down a sometimes counterintuitively branched logical rabbit hole of the state of predictions.

\section*{ 2017.01.29at11:52 }
\subsection*{ I love science because... }
I love science because all of the wonderful things it does.
What is being said with the word "because" in the previous sentence?
One interpretation could be that the sentence just makes one feel good.

On analysis, however, we get to the good stuff.
That is the fun and other forms of utility are maximized.
I want to be reading about python's natural language processing module.

I have this belief that if I love Jenna then I should say something now because what if she marries Alex?
I should lay everything on her as the hero of my own story could be heroically romanticized to do.
I should say only the friendliest, warmest things because that is what the hero of my story will do.

I simply want to get Jenna's excitement about topics scientific.
This want is because I've experienced how energizing and pleasing it is to be adored by Jenna. 

\section*{ 2017.02.24at18:59 }
\subsection*{ Make time to read me. }
2018.01.31at20:09 What a tease I am!

\section*{ 2017.02.24at21:35 }
\subsection*{ workHere }
Cluster descriptions of Sustainable and Healthy Community's(SHC's)tools in a space $\mathbb{S}=$ roles $\times$ subroles $\times$ fundamental objectives $\times$ objectives $\times$ concepts.
Vary the number of clusters used in a k-means algorithm within $\mathbb{S}$.
Give clustering data and code to the developers of Decision Path Library(DPL).
This tool can be a means of crowd-sourcing the development of DPL by informing the DPL's labeling of points in $\mathbb{S}$ with concepts.

DPL can utilize the feedback users give that additional labels are desired.
The SHC-Tools-Inventory webapp can use the DPL's labels and allow users to seve tools and dismiss tools from the cart.
Tools that strongly correlate weak cart-scores with some subspace $\mathbb{S}'$ of $\mathbb{S}$ tell DPL not to specify $l$ in $\mathbb{S}'$.
Weak cart-scores indicate lack of accuracy in mapping concepts to tools. 

A weak cart-score is a small ratio of cart-additions to total suggestions of the label.

\section*{ 2017.03.30at21:34 }
\subsection*{ Make a million dollars right now. }
I propose this for as soon as I get a chance: begin my fortune by going to Ryan, Sutie's grandson-in-law who works at Google, with the idea for Google to make a collaborative compositional tool used to create beautiful openly sourced music and collaborative educational masterworks of mastery from many masters' remasterings.

\section*{ 2017.03.31at23:53 }
\subsection*{ Jenna }
Jenna, I've been thinking about you.
I've decided a thousand times what to do.
I have resolved to come down to California, where I saw you were going to school on your Facebook profile.
I want to wish Alex the best because he is the man you've chosen.
Complete is the only respect I will show your opinion.

\section*{ 2017.04.01at01:49 }
\subsection*{ millionDollarIdea }
Go to Microsoft as a partner in making an interface that's accessible from this beautiful keyboard thing.
Go to Google about reimagining Google Play as an instrument on the web;
that is an instrument through which anyone connected to the web can compose music, respond to compositions, AA

\section*{ 2017.04.18at17:29 }
\subsection*{ mathouts }
Using the limits upon which calculus is based allows determing the limit as an operation is composed of itself unboundedly many times.
All operations are functions.
My mathematics needs a notation for a unary operator signifying a specified number of recursions.

This notation is a foundational element of a language with which logical machines may be constructed.
It allows me to carry any solution I've discovered to any language I please.
This tool permits a mathematical language that allows describing algorithms.

This description of the algorithm could serve as part of a deliverable that a software engineer would sell.
An engineer could deliver an independent description of the requirements of the solution delivered.
A solution delivered along with its description could then be implemented in any language anywhere its application provided utility to some player.

\section*{ 2017.05.07at10:38 }
\subsection*{ Create a cool name for a function that reads a beautifully typeset letter to yourself. }
One fitting name is readme.

\section*{ 2017.05.09at21:52 }
\subsection*{ Please get a workflow going to journal from the laptop. }
It is desparately urgent that I get a workflow where I can journal from my laptop.
I know that I can merge two divergent journals together without loss of ordering info.

\section*{ 2017.05.16at20:54 }
\subsection*{ Please get a workflow going to journal from anywhere via url. }
I need to find a louder method of sending messages myself.
If I actually read this conversation with myself that I always have in my head while writing and never write down then I would have a beautiful picture of the shape of my cogitation.
I can refer back to my journal as I write a song that reflects the beauty of the universe around me.

\section*{ 2017.06.28at16:14 }
\subsection*{ ideas to read and act upon immediately }
I want to turn my patio into a greenhouse.
The walls to my yard could be reclaimed windows from between first and second street kitty corner to the Beanery in downtown Corvallis.
I want to replace the carpet with sheet vinyl.

\section*{ 2017.06.28at16:22 }
\subsection*{ Things I want to write about. }
I want to write about preparing and eating food as an act of self-love. I want to write a simple introduction to the trunk of Science, Technology, Engineering, and Mathematics(STEM). I want to write about humans' rightful stewardship of the culture of plants, animals, bacteria, and fungi humans exist through.

\section*{ 2017.06.29at17:39 }
\subsection*{ My trajectory through the science of food. }
I believe I have found my greatest ability to reduce suffering through the scientific harvest, preservation, and preparation of food. I have never believed that I would contribute through the greatness of my abilities. The things I have found to save human lives are simple.

People can experience unkown joys through the flavors, satiation, and fitness gained from eating and hence being well. They say you are what you eat. They also say diet is 80% of health and exercise is the complementary 20%. This reinforces the message from before: eat to be well.

Fermentation is proper preservation. Seeds are a good substitute for refined oil. Refined suger causes immediate spikes in blood-pressure. Equivalent amounts of sugar in the form of whole plants contain fiber which is beleieved to stabilize blood pressure upon ingestion.

\section*{ 2017.07.02at22:46 }
\subsection*{ These last couple of days have been worth more than I will ever be able to afford. I thank those who have brought all my joy forth. }
I have babbled at people through my haze of drunk with love for them. I wish I could remember everyone's name. Here goes an attempt to recount what I've found.

I feel gifted by a confident delivery of a dance. This dance was exemplified by Damon's newfound singing, Sequoia's beautiful voicings, and a nameless shredded man's literally literal dancing. I felt loved the whole time by Jonnny's accepting and guiding presence. Jonny acts so admirably that it sets a sterling example for how to let be. Let be as in let everyone else be and tend to themselves by confidently being me.

When was the last time I ever felt so good? I would recall if I only could. So many smiles to reflect that my face feels too small to see all these smiles while returning them all.

I wish for nothing now as lay to sleep this good night. I hope not only to lift these people with my life, but maybe I can bring them into some others' sight. Face cracking smiles make entire lives' worth of smiles seem led to be left to all right.

I need to use the Maillard-reaction and fermentation show veganism to feel nice. This is shown to herbivores and carnivores at nothing but just the the right kind of price. I cannot even dream of someone not finding great food to come from just beans, dark green leafies, and whole grains like oats, rye, wheat, and rice.

I don't hope to hurt any more things than I have already by being where I be. I hope to remember to allow everyone the original sin of doing what they've done. Just as we have all evolved from our whole ancestry, I give when I remember the grace of loving all versions of me.

Gifts I have for my friends are the messages of a healthy way to be. I hope to live so that those close can see a shining example of this life from me.

\section*{ 2017.07.24at06:35 }
\subsection*{ This is a great idea for research in education. }
Students could be tested on their knowledge by teaching others. Many say real learning occurs when teaching others. Let us put this thought to the test in a way that allows education to pay for itself.

The cost of education is reduced to the time it takes to measure teaching. I expect this method will engender students' feelings of solidarity, appreciation, and admiration toward teachers. Students also take on the jobs of many teachers. This job-taking is proper form of subsidy for education: a subsidy that benefits the educators and the students. Social barriers to teaching may be eliminated through research driven via this means.

Students can learn from lessons developed to the standards of what is expected to be taught. Using recorded lessons lets us greatly objectify and optimize tutelage. Teachers may experiment with different presentation styles and orderings via this means.

I see losing jobs in teaching. I see gaining work in experimenting with improving education. Jobs that consist of reciting lecture material are replaced with the work.

Work is needed planning the order of topics. Work is needed creating alternative styles of presentation. Work is needed analyzing the data for continuous integration of results. These analyzed results may inform future work in planning. This gives a cycle which may be arbitrarily reduced with proper attendance to the statistics I hope will become a standard subject for all members of the population to one day be taught because statistics gives great power to science hence scientists hence consumers of the benefits of science.

Varying presentation style can become a distributed task. This allows us to leverage the abundant population for data from research on optimizing education and learning. Learning gains interest as a topic of research because machines can help us learn how to learn better by testing models of learning.

For example, neural networks could be built to model patterns of learning. Rates of learning may then be objectively tested by comparing rates of convergence in accuracy between different models.

\section*{ 2017.07.24at07:11 }
\subsection*{ Subsidizing education is help we can give those suffering. }
Using methods oulined in 2017.07.24at06:35 can extend an extremely cheap and effective education to people in need. Education is claimed by many to be the best help that may be given to the "impoverished." Present video lectures for free as research education. Request donations of data on the performance of students-turned-teachers.

There is only a need to demonstrate the power of the tools being taught to motivate students to learn. Illustrate power by first modeling some system simply. Subsequently optimize that system by bijection within known bounds. This optimization strategy converges to correctness in a logarithmic number of trials given some pair of known bounds and a desired precision of accuracy.

\section*{ 2017.08.06at17:14 }
\subsection*{ Develop these topics for Drew. Write them in a book. #book}
\begin{itemize}
    \item derive the unit circle \begin{enumerate}
        \item fix one end of a circle to a point and rotate the taught end of the other one revulution to draw a circle
        \item define one radian to be 
    \end{enumerate}
    \item make sourdough
    \begin{enumerate}
        \item make starter
        \item mix two parts flour to one part any other dry ingredient
        \item add water to desired consistency
        \item turn dough
        \begin{enumerate}
            \item show each turn doubles the number of layers
            \item demonstrate 20 turns is more than a million layers
        \end{enumerate}
        \item ferment dough overnight
        \item knead again
        \item explain gluten formation
        \item explain effect of kneading on protein matrix
    \end{enumerate}
    \item make saurkraut
    \item demonstrate honey fermenting in water
\end{itemize}

\section*{ 2017.10.10at18:52 }
\subsection*{ book: early dialogue }
- foundation
  - definitions
    - simplicius: what questions can we meaningfully ask?
    - ontology: what is true?
    - simplicius: something is not nothing.
    - math: this is written $1 \ne 0.$
    - simplicius: and...
    - math: increasing something is not the same as neglecting that thing.
    - simplicius: what use is this?
    - math: build counting by increasing the number of things.
    - simplicius: how?
    - math: increase nothing by one something to one something. Increase one something by one something to two things. Increase as desired.
    - simplicius: what can I do with this?
    - math: build multiplication from counting the same amount repeatedly.
    - simplicius: more work?
    - math: build exponentiation by multiplying by some base number a number of times.
    - simplicius: ...
    - math: define the imaginary basis $i$ to be $i=\sqrt{-1}$ in order to give closure under the operation of exponentiation.
    - simplicius: what is closure?
    - math: a group is a set with an operation defined that maps all arguments from the set back into the set.
    - simplicius: why should I care?
    - math: closure provides groups with some amount of certainty in delivering interpretable results of modeled phenomena.
    - simplicius: what is this modeling thing you speak of?
    - ontology: define science as making and testing testable predictions. A prediction is a model describing the expectations of a test.
    - simplicius: why does that seem like a good idea?
    - philosophy: when tests are defined then improving a test's prediction improves knowledge of the defined system.
    - simplicius: does that even mean anything?
    - philosophy: it means for any defined resources predictions can be made about how to harvest resources while maintaining future availability of resources.
    - simplicius: what motivation do living things have to harvest resources while maintaining future availability of resources?
    - philosophy: this is a definition of sustenance.
    - simplicius: who defines sustenance as positive?
    - observation: all living systems systems implicitly define sustenance as positive by expending the effort required to continue living.
    - simplicius: this is important?
    - ontology: you agree this is important with every next breath and the fact you haven't missed one yet.

\section*{  }
\subsection*{ #writtenWithBlahScript }
I am excited at the idea of blabbing into a mic at night then transcribing my words after meditating upon the ideas previously left from me to me on nights before while warming up the food that's me so I adore so heat and eat for all my evermore.

\section*{ 2017.11.14at07:06 }
\subsection*{ article: On the Evolutionary Utility of Cancer }
\begin{itemize}
  \item trauma is correlated with carcinogenesis#cite.
  \item cells are genetically heterogeneous.#cite
  \item are modeled as genetically evolving only through sexual reproduction.#cite
  \item are observed to undergo somatic evolution by natural selection within an organism.
  \item trauma can be a pathological indication of an emerging environ.
  \item known causes of cancer are abruptly emergent environs.
  \item many organisms have been exposed to the environmental toxins associated with increased incidences of primarily gonadal cancers?(A review of the role of emerging environmental contaminants in the development of breast cancer in women)
  \item emerging exposures to substances at toxic densities primarily affect the location where sex cells are produced in organisms modeled to genetically evolve through reproduction.
  \item is considered necessary for utilization of the prefactors of bioavailable vitamin D.
  \item of melanoma doubles with five sunburns.(#cite Timing of excessive ultraviolet radiation and melanoma: epidemiology does not support the existence of a critical period of high susceptibility to solar ultraviolet radiation-induced melanoma.)
  \item many hominids have exposure to cigarette-smoke?
  \item cancers' incidences are correlated with emerging environs:
    \begin{itemize}
      \item develop lung-cancers.
      \item who breath asbestos develop mesothelioma, a telling form of cancer, in the lungs.
      \item who chew develop oral cancers.
      \item who get burned by the sun develop skin-cancers.
      \item who eat toxins develop cancers in the gastrointestinal tract.
      \item who experience chronic trauma to a location experience local tumorigenesis.
    \end{itemize}
  \item ...
\end{itemize}


\section*{ 2017.11.18at19:17 }
\subsection*{ book: entities exist similarly to how organisms live }
Generalize from life to autonomous entities. Hence fires, companies, cancers, storms, languages, intentional machines, conformations by material or immaterial means, and various other nonliving systems may be classified in a taxonomic system which categorizes self-organized systems together as entities.

\section*{ 2017.11.20at21:53 }
\subsection*{ Book: Knowledge Network }
The knowledge I want to deliver can be idealized as the nodes of a mathematical network of ideas linked by dependencies.
Build math from fundamental equations.
Describe functions while describing math as these things we have been interfacing all our existences: the gum-ball-machine, a spouse, and other probability density functions.

State-machines are really just functions.
A state-machine maps all of its input to its trajectory in a state-space.
How is this characteristic distinct from any other being?

Sets are collections of things.
The union of sets contains every element of each set unioned.
The intersection of sets contains all elements contained by all sets interrsected.

Distinguish words.
Synonymity is a smell of the uninformed mind.
People would not have made distinct words in the same language for the same thing.
Add depth to the palette of vocabulary with etymology.

Neural networks are beings that learn to do many tasks better than any human.
This thought hearkens back to functions. Now a function replaces a human input of feature-extraction with stochasticity in improving itself.

\section*{ 2017.12.09at22:22 }
\subsection*{ On Human Clones }
Humans are macroscopically distributed colonies of cloned autonomous organisms that are each at differentiating positions in Waddington's epigenenetic landscape. A human colony sometimes carries around some autonomous haploid organisms known as gametes. If these automata can conspire to create conscious consensus of unity and oneness then who stands in the way of an collaboration on the next layer of abstraction? I mean a society of colonies that can play together as my bodily self those individuals I consider the rest of me.

\section*{ 2017.12.10at20:06 }
\subsection*{ book: Humans are a device to further a symbiosis between incident yeast and bacteria as evidenced by wonderful feelings caused by pointedly specifically created compounds, particularly alcohol and DMT, that make humans feel wonderful. }
A human being is a consciousness that exists associated with a colony of various bacteria, various fungi, many differentiated clones of a single homo erectus diploid cell, and sometimes gametes. I specify the consciousness because that is the only person we have communicated with that I know of. Maybe someone should do an experiment to try to interact with an unconscious person.

Consciousness implies that some of the cells are alive. I have imagined and so lived conversations with my dead sister. I encourage anyone who has lost somemone to not do that person the disservice of never being allowed to speak to you again simply because his or her homoerectus cells are dead.

I want to write a letter to a biophysics journal explaining a way that they are the beautiful and living body of knowledge that is science. It will be a message of love. I don[t know why I convince myself that I don't type quickly.

I am just so F-ing glad Dr. Michael Greger has finally said this. I have to make a Facebook right now.

\section*{ 2017.12.12at11:56 }
\subsection*{ book: Elucidating a Definition of a Human }

\section*{ 2017.12.12at21:01 }
\subsection*{  }
I sit here dreaming about 1,000 different ways I could be better. I know enlightenment shows us that there's no need to assign value to one way or another. There is no need to call the way I am in dreams a better or even different me. Be the beauty that I dream I've seen and so I know is sweet.

\section*{ 2017.12.12at2 2:31 }
\subsection*{ lifeplan: justWrite }
I want to start a restaurant that cooks for people out of love. I want to make cheese from a responsible substrate. I want to ferment in stages and cycles. I want to do this as a bed and breakfast.

I want to host artists who come to make art as a trade for their stay. Their work can be in a gallery to raise money for local charities. Some of the art can decorate the restaurant.

The restaurant only sells locally grown produce. I sell prepared ingredients to take and make in bulk. I also sell education vacations to people who want to learn to make healthy delicious foods to feed those they love.

The restaurant can show people kitchen skills as their food is being prepared. The diners could practice making food for charity. That is, the diners can submit a test batch of prepared food as a free test of the taught kitchen-skills so that the food may feed others as charity.

There will be a pollinator-garden with offering opportunities for education. There will be fungus in the garden. There will be a forest on the garden.

I want to write while doing all of this.

\section*{ 2017.12.13at21:45 }
\subsection*{ book: Intentionally evolving to nurture life }
Cancerous cells are characterized by 10 cellular hallmarks of cancer(Weinberg and Hanahan, 2000 and 2011) that are descriptive of the ways people have abused their environments and formed empires to spread this ecological disregard by securing additional resources.

\section*{ 2017.12.15at00:59 }
\subsection*{ write a children's book }
I want to write a childrens' web-page in the style of a children's book that depicts a cycle that gets an energy-input from the sun to the primary-producers and through the energy-web of life and more general entities.


\section*{ 2017.12.15at21:24 }
\subsection*{ book: topics to cover }
Investigate the analogy between photosynthesis and cooking. Analyze the chemical reactions that may deepen the analogy if affected while cooking. The input of energy is from burning plant-matter, decomposing plant-matter, or the Sun's incidence and entrance into a plant.

Plants may be replaced by alga. Alga may 

\section*{ 2017.12.16at16:37 }
\subsection*{ Talking with Lee Aspitarte about blockchain and git }
Lee is working a post-doc in NETL. We have agreed to create a neural network to do financial trading through cryptocurrency-assets.

\section*{ 2018.01.23at14:50 }
\subsection*{ a great life's work }
Author a childrens' site sharing with the world math, science, our microbial selves, humans viewed as mutualistic symbiants of plants. Make the site accessible through proper use of web-technologies. Make the inforamation accessible cognitively by presenting it to children. Refer to 2017.12.15at00:59 for more on this.

\section*{ 2018.01.26at21:07 }
\subsection*{ A children's site }
Investigate how self-organizing-systems turn themselves into self-perpetuating-systems.
Share this on a children's site.

\section*{ 2018.02.03at15:31 }
\subsection*{ Plan for near future }
Make a software development entity into a highly valued thing.
Make Nearly Normals or really any other restaurant placed somewhere nice like near a school that teaches people to code free for lunch so that more people can accomplish sprints for their food and they can see how food is made correctly.
Make a software development entity by trading meals for code.
Buy Nearly Normal's and be the chef by showing people how to prepare things for themselves.
Make an entity named "Gift to the World" where coders get together and eat lunch sprinting on open source publicly licensed projects in return for food credit for them.

\section*{ 2018.02.03at17:35 }
\subsection*{ Work at Interzone as its owner. }
Buy Nearly Normal's.
Work at Nearly Normal's preparing and serving that meal's food.
Do it now.
Make preparation of food a show for all to see a wonderful way to be healthy and happy whenever not fasting.
Emphasize the different states between sometimes experiencing prolonged fasting and never fasting. 
Show the body-composition people can acheive by simply living healthfully.
Show the beauty of the space that can be made by a beautiful stewardship focused on positive biologicl feedback.

Make the place a museum showcasing the food at every stage.
Show a living pantry.
Make the place a musical treat.
Create music for the house.
Show people how to ferment.
Do the work as a performance and be an intentional living coach.

Make Nearly Normal's outdoor location a magical increasingly forested exhibit of harboring local ecological health by adding orginalic matter, propagation, guilding, pollinator housing, and suspending pollinator-supporting epiphytes with cleverly arranged ropes.
Tell people the benefits of buying local include the ability to minimize waste through transportation of supplies and to localize ownership of supplying the nutrients feeding locals instead of mindlessly mining the environment with no way to ensure agreeable practice by the disregard enforced through distancing.

\section*{ 2018.02.04at00:19 }
\subsection*{ Rename Nearly Normal's Improving Normalcy or something meaning the same thing maybe more k-literately by expressing konstancy: aliteration with a k. }
Perform by showing how to prepare a meal and perform as a person hosting others to a healthy lesson with a healthy and hearty meal.
Sell previously prepared meals in a jar as would be preserved in a cellar and then heated via compost to eat.
Show how to heat via compost as a reward for farming organic matter into a usable state for the soils housing plants an carbon-seqestration-mutualistic-symbionts.

\section*{ 2018.02.05at13:28 }
\subsection*{ moments of clarity to include in a book }
I had a moment of clarity when Sterling's advice to be immodest with conditioner when dealing with my tangles shown clearly true. I want to investigate using oils toand natural broducts to work knots out of my hair. The trick is to use extra conditioner and work directly on knots by rubbing the knots vigorously as though to flatten them out.

I had a moment of clarity that showed me the folly of spending time and energy on food and venue at my private residence. The folly is that I could easily capitalize on these efforts by putting this energy into the same things at a restaurant. I have decided to buy Nearly Normal's so that I can put all this energy into a presence on Monroe. I want to investigate zoning the restaurant to have a living space on the site.

\section*{ 2018.03.03at20:11 }
\subsection*{ recipe: healthy preparation of grains, nuts, seeds, and beans and other legumes }
Steps are listed in the order they are undertaken.
Each step may be modified or omitted as desired.
Steps attempt to include their utility to inform modification upon implementation.

Sprout ingredients by the following process.
Submerge at least 8 hours.
Pour off water and let stand at a warm temperature in the presence of oxygen to induce sprouting.
Rinse daily to flush accumulating mold.
Harvest sprouts before they green to avoid toxins which protect the sprout from predators.

Ferment ingredients using the following process.
Combine ingredients with woody vegetables, starchy vegetables like tubers and grains, colonizing ingredients, and any desired backslop.
Submerge ingredients in up to three times their volume of salted water.
Agitate the mixture as desired to aid fermentation and remove byproducts such as CO2 and methanol.
Allow to progress as far as desired in this state.

Cook the mixture using the following process.
Rinse the mixture of mathonol, phytates, and acid.
Ensure the mixture is 70\% water.
Cook in a pressure cooker for an hour at pressure and let cool under pressure.

Ferment the mixture with the following process.
Mash mixture.
Add backslop or otherwise colonize mixture as desired.
Let stand for desired duration.
Rinse of phytates and methanol before consumption.

\section*{ 2018.04.27at01:59 }
\subsection*{ Fasting since the night before learning my time with EPA is ending }
I decided to observe a water-fast for 40 days after eating dinner on 2018.04.12.
The protocol for this water-fast planned to ingest only water.
I decided about four days into the fast to limit my consumption to the hours when the sun was not visible over the horizon in the spirit of Ramadan.

I continued this protocol of taking in only water between dusk and dawn until 2018.04.26.
The fast was interupted by a dinner made from vegetables I had been fermenting for weeks.
Mushrooms grown in the kitchen of the trailer I named Old No. 7 were added during the last several days of fermentation.
The fast-ending-meal was cooked in ramekins I purchased with Old No. 7.
The ramekins contained the ferments, a squash I had quartered, as well as chard and spearmint from the garden.

This garden at Old No. 7 was in the raised bed I built from urbanite.
Urbanite is a name for repurposed concrete refuse.
I collected the cocrete from the region around Corvallis.
I broke the urbanite into usefully shaped blocks with a hammer and chisel.

There was a giant feast binge-ginning at lunch on 2018.04.26 and continuing through the following day 2018.04.27.
This binge-ginning of the feast was purchased during my lunch-break from EPA's Western Ecology Division between 14:35 and 16:35 during a ten hour workday after which I departed the office 2018.04.26 at 22:00.
The feast began with a salad including cooked greens, carrots, brocolli, and mushrooms.
The feast ended with pancakes made of white flour, corn-flour, grape-jelly, and a small amount of baking soda and yeast 2018.04.27 at 06:00 after staying up all night.
I slept until 09:00 then went back to work.

\section*{ 2018.06.08at09:23 }
\subsection*{ Create and study powering pumps with incident sunlight or geothermal heat to move fluids such as air or water. }
I believe an appropriate coloring with black and white could potentiate and therefore force water in a particular direction within a pipe in the sun.
The black and white regions are in my mind a simple way to get a first order control over the amount of heat delivered to the fluid within the pipe.:
I hope to investigate the possible connection between rotation of fan blades about their individual axes.
I suspect direction of fluid flow could be determined by embelishments of the surface of the interface between the black regions and the white regions.

Some fans are made of a central rotating body which has blades protruding radially outward from the center of rotation of this central rotating body of the fan.
Each blade is rotated about its axis.
There is a seeming relation between the geometry of this type of fan and the design of the black and white regions of a pipe which might impart a directional bias to the movement of the particles within the pipe.
I suspect study of the isometry between the tesselation of the black and white regions of a pipe and the configuration of the blades of a fan might reveal means of patterning the pipe to create a bias in the flow of the fluid within the pipe.
Potential applications include air-exchange in indoor environments, irrigation, long-distance movement of water.

\section*{ 2018.06.08at13:53 }
\subsection*{ Heat a reservoir of hot water with sunlight. }

\section*{ 2018.09.02at00:54 }
\subsection*{ One for the Menu: Tonight's Recipe for Tomorrow Night }
Tomorrow night I will again cook tonight's raisin and almond pilaf adapted from page 101 of The Ultimate Cooking Course and Kitchen Encyclopidia by Norma MacMillan and Frances Cleary.
Tonight I burned the almonds and failed to saturate the rice fully with water.
I plan to do things perfectly tomorrow by having everything ready.
The pilaf was so wonderful that I am excited to serve the experience to those interested in eating and being deliciously healthy.

Raisin and Almond Pilaf:
\begin{enumerate}
  \item Gather and prepare:
    \begin{itemize}
      \item 3 tablespoons avocado oil
      \item 1/4 cup sliced almonds
      \item 1 small onion
      \item 1/3 cup raisins
      \item 5/4 cups long-grain rice
      \item 5/2 cups boiling vegetable-stock
      \item salt and pepper
    \end{itemize}
  \item Start a vegetable-stock.
  \item Blanch, skin, and slice almonds.
  \item Mince the onion.
  \item Heat saucepan to medium on stove.
  \item Fry almonds to golden brown then remove almonds with a slotted spoon.
  \item Add onions then fry them until soft.
  \item Add raisins and rice then fry everything until rice is slightly tranlucent.
  \item Add the stock, boil, cover, then cover the saucepan and cook on very low until the tender rice has absorbed all the liquid.
  \item Add salt and pepper to taste then fluff in the almonds.
\end{enumerate}

  "One for the menu" means that I intend to add this to the menu of experiences I offer.

  I want to invent a perpetuity in the form of a restaurant that serves the produce of it's spaces as a way to preserve those spaces in a form healthy enough to feed people.
  One example would be a forested garden which yields its nuts, seeds, beans, greens, grains, fruits, vegetables, ferments, and fungi to its visitors.

  \section*{ 2018.09.02at01:23 }
  \subsection*{ Invite People to Privately Catered Events }
This could grow to be something as wornderful as a fair financially fueled by feeding people health.

\section*{ 2018.09.02at01:47 }
\subsection*{ A Restaurant as an Ecosystem's Protector. }
A restaurant is a financial entity that could own the land that produces food and the food's lineage.
Lineage could be horicultural and grastronomic descriptions of ingredients for items on a menu.
The menu would then contain the story of each ingredient's lineage.
This story would exemplify preserving an ingredient's delightful evolution.
